---
title: "MC_data_cleaning"
author: "Sydney Wood"
date: "2023-07-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 


#### Load Packages 

```{r}
library(tidycode)
library(tibble)
library(dplyr)
library(tidyverse)
library(glue)
```
# Make data files

#### data_Key 
TODO 
1. assign random identifier to all students in the course 
2. write file with key of anon_id to student id
3. write all files replacing student id with rand-id and remove all other identifying info 


#### Demographic data 

In the commented code: import raw data and get only the columns of relevence. rename colums for ease. write file with the cleaned data

```{r}

dem_data_raw <- read.csv("Raw_dem_data_anon.csv", sep =",")


dem_data_short <- dem_data_raw %>% select("anon_id", "consent", contains(".."))



#colnames(dem_data_short) <- c("ID", "student_id", "consent", "age", "year", "gender", "int_student", "esl", "e_exp", "e_lvl", "ethnicity", "p_education", "m_education", "par_rel", "fin_support", "ses", "grant", "soc_med", "hw_time", "transfer")

#write.csv(dem_data_short, file = "WQ23_dem_data_shortened.csv")




#dem_data <- read.csv("WQ23_Dem_data_cleaned_anon.csv", sep = ",")


#change categorical data to factors
dem_data <- dem_data %>% mutate_at(c(5,6,7,8,11,14, 16,17, 20), factor)

#take only consenting student data
dem_data <- dem_data %>%  filter(consent == 1)

# create variable first gen
dem_data <- dem_data %>% mutate(first_gen = case_when(p_education < 4 & m_education < 4 ~ 1, p_education > 3 | m_education > 3 ~ 0))

#write data file with cleaned data (should also have both student_id and anon_id)
write.csv(dem_data, file = "WQ23demographicsFull.csv")


```



#### Grades data (Canvas)

```{r}
wq_grades <- read.csv2("wq23FinalGrades.csv", sep =",")

####Calculate grades 

wq_grades_short <- wq_grades %>% select("ID", "SIS.User.ID", "Exam.1..965996.", "Exam.2..965997.", "Exam.3..965998.", "Exam.4..965999.", "Exam.5..966000.", "Final.Exam..966002.", "Prep.Participation..up.to.250.points..Final.Points", "Extra.Credit.Final.Points", "Exam.Corrections...966001." ) %>% mutate_at(-c(1,2), as.numeric)


colnames(wq_grades_short) <- c("ID", "student_id", "exam1", "exam2","exam3","exam4","exam5","exam6", "prep_p_raw", "extra_credit", "e_correct")


###Prep and participation max points
wq_grades_short$p_p_final <- wq_grades_short$prep_p_raw
wq_grades_short$p_p_final[wq_grades_short$prep_p_raw >= 250] <- 250


##drop lowest exam total
wq_exams <- wq_grades_short %>% select(contains("exam"))

wq_exams$lowest <- apply(wq_exams, 1, min)

wq_exams$lowest <- wq_exams$lowest * -1

wq_grades_short$exam_total <- apply(wq_exams, 1, sum)



##Course grade

final_grade_calc <- wq_grades_short %>% select("extra_credit", "p_p_final", "exam_total")


wq_grades_clean <- wq_grades_short %>% 
  mutate(final_grade = apply(final_grade_calc, 1, sum)) %>%
  mutate(opt_in = case_when(e_correct == 0 ~ 0, e_correct > 0 ~ 1)) 


###Turn 0 into NA on exams 


wq_grades_clean <- wq_grades_clean %>% mutate_at(c(3:8),~na_if(.,0) )

exam_col <- wq_grades_clean %>% select(contains("exam"), -exam_total)

#function to get the % score for each exam 
div <- function(x) ((x/150) *100)

wq_grades_final <- wq_grades_clean %>% mutate_at(colnames(exam_col), div) %>% mutate(exam_total = (exam_total/750)*100) %>% mutate(final_grade = (final_grade/1000)*100)


write.csv(wq_grades_final, file = "wq_grade_data.csv")

```


### Written Exam Data 

Very very messy brute force solution. I recomend finding a better solution- 

}
## only written Qs data
###run for each exam separately 


setwd("~/GitHub/MC_data_cleaning/2023 data")

##version a 
w_exama <- read.csv("5_A_Mar23.csv") #I manually changed the file name for each exam

w_exama <- w_exama %>% select("SID", "Status", "View.Count", 14, 19,23, 24, 25, 29, 30, 31) #these change for each exam as well 
  
q_names <- c("student_id", "status", "views", "pv_op", "cv", "cv_compare", "confound", "internal","interpret", "external", "replication")

colnames(w_exama) <- q_names

w_exama <- w_exama %>% filter(status != "Missing") %>% select(-"status")

## version b
w_examb <- read.csv("5_B_Mar23.csv")
w_examb <- w_examb %>% select("SID", "Status", "View.Count", 14, 19,23, 24, 25, 29, 30, 31)
  
q_names <- c("student_id", "status", "views", "pv_op", "cv", "cv_compare", "confound", "internal","interpret", "external", "replication")

colnames(w_examb) <- q_names

w_examb <- w_examb %>% filter(status != "Missing") %>% select(-"status")

## version c
w_examc <- read.csv("5_C_Mar23.csv")
w_examc <- w_examc %>% select("SID", "Status", "View.Count", 14, 19,23, 24, 25, 29, 30, 31)
  
q_names <- c("student_id", "status", "views", "pv_op", "cv", "cv_compare", "confound", "internal","interpret", "external", "replication")

colnames(w_examc) <- q_names

w_examc <- w_examc %>% filter(status != "Missing") %>% select(-"status")

## version d
w_examd <- read.csv("5_D_Mar23.csv")

w_examd <- w_examd %>% select("SID", "Status", "View.Count", 14, 19,23, 24, 25, 29, 30, 31)
  
q_names <- c("student_id", "status", "views", "pv_op", "cv", "cv_compare", "confound", "internal","interpret", "external", "replication")

colnames(w_examd) <- q_names

w_examd <- w_examd %>% filter(status != "Missing") %>% select(-"status")

w_exam <- rbind(w_exama, w_examb, w_examc, w_examd)

write.csv(w_exam, file = "exam5_writtenQs.csv")





### Combine Written and Full exam scores 


1. read in each written exam file 
2. calculate the % total for each 
3. add only those columns to the final grades data 
4. save a final_grade_data



#### Combine data 


```{r}
#read in final_grade_data
#

full_grades <- wq_grades_final %>% select(-"ID")

full_data <- full_join(dem_data, final_grades, by = "anon_id")

full_data <- full_data %>% filter(!is.na(consent))

full_data <- full_data %>% select(-"ID", -"consent")

write.csv(full_data, file = "cleaned_data_no_qual.csv")
```







