---
title: "NPB Collaboration Analysis Plan"
author: "Sydney Wood"
date: "2024-09-17"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Descriptives

Summarize the characteristics of the sample. Especially first generation status, native language, english proficiency, SES and racial composition.

# Confirmatory analysis Multilevel Model

## Creating fake data for analysis

```{r}
packages <- c("ggplot2",  "tidyverse", "apaTables", "colourpicker", "dplyr", "gridExtra", "knitr", "lme4", "reshape2", "stargazer", "gtsummary", "performance", "afex", "jtools", "svglite")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
```

```{r}
anon_id <- c(1:300)
section <- sample(1:12, 300, replace = T)
TA <- sample(1:3, 300, replace = T)
Exam1 <- rnorm(300, mean = 80, sd = 5)
Exam2 <- rnorm(300, mean = 85, sd = 7)

fake_data <- data.frame(anon_id, section, TA, Exam1, Exam2)

fake_data <- fake_data %>% mutate(TA = case_when(section == 1 ~ 1, section == 2 ~ 1, section == 3 ~ 1, section == 4 ~ 2, section == 5 ~ 2, section == 6 ~ 2, section == 7 ~ 3, section == 8 ~ 3, section == 9 ~ 3, section == 10 ~ 4, section == 11 ~ 4, section == 12 ~ 4))

fake_data <- fake_data %>% mutate(condition = case_when(section == 1 | section == 5 | section == 11 | section == 8 ~ 1, section == 3 | section == 9 | section == 4 | section == 10 ~ 2, section == 2 | section == 6 | section == 12 | section == 7 ~ 3))

fake_data_long <- gather(fake_data, key = "obs",value = "score" , Exam1, Exam2)


```

I didn't model any shared variance in the nested grouping structure so the proposed models will report singularity. This is very unlikely to occur in the real data, even if there are no inherent differences between discussion groups. Therefore the code for fitting the model is commented out

## Confirmatory Analysis

```{r}

eq0 <- (score ~ obs + (1|anon_id))
#mod0 <- lmer(eq0, data = fake_data_long)
#summary(mod0)



eq_5 <- (score ~ obs + condition + (1|anon_id))
#mod_5 <- lmer(eq_5, data = fake_data_long)
#summary(mod_5)


eq1 <- (score ~ obs*condition + (1|anon_id))
#mod1 <- lmer(eq1, data = fake_data_long)
#summary(mod1)


eq2 <- (score ~ obs*condition + (1|anon_id) + (1|anon_id:section))
#mod2 <- lmer(eq2, data = fake_data_long)
#summary(mod2)

eq3 <- (score ~ obs*condition + (1|anon_id) + (1|anon_id:section) + (1|anon_id:section:TA))
#mod3 <- lmer(eq3, data = fake_data_long)
#summary(mod3)
```

#Exploratory analyses

These models and analyses will be created post hoc as we do not have specific hypotheses regarding effect of various demographic or course related variables.
