---
title: "2024 Data"
author: "Xinhui Zhang"
date: "2024-09-04"
output: html_document
---

# libraries
## Libraries and Packages
```{r}
# Package names
packages <- c("ggplot2",  "tidyverse", "apaTables", "colourpicker", "swirl", "dplyr", "gridExtra", "knitr", "lme4", "reshape2", "stargazer", "colourpicker", "afex", "jtools", "glmmTMB", "lavaan", "plm", "sandwich", "naniar", "coefplot", "ggpubr", "glue", "olsrr")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
```


# Import data 

```{r}

data <- read.csv(file = "~/GitHub/MC_data_cleaning/2024 Data/2024_full_data_cleaned.csv")

data <- read.csv(file = "~/GitHub/MC_data_cleaning/2023 data/new version of exams/2023_cleaned.csv")

#data <- data %>% rename(e_internal = e_correct)



```



## Demographic Data 


```{r}


data <- data %>% mutate(URM = case_when(ethnicity <= 2 ~ 1, TRUE ~ 0))


##Assign Factors
data$first_gen <- factor(data$first_gen)
data$URM <- factor(data$URM)
data$int <- factor(data$int)
data$gender <- factor(data$gender)


data %>%  group_by(opt_in) %>%
  summarise(var = "optin", n = n())

##First Gen 
first_gen_table <- data %>% group_by(first_gen) %>%
  summarise(var = "first_gen", n = n(), percent = (n()/429))


first_gen_table

first_gen_table_int <- data %>% group_by(first_gen, opt_in) %>%
  summarise(var = "first_gen", n = n())


first_gen_table_int



##URM
URM_table <- data %>% group_by(URM) %>%
  summarise(var = "URM", n = n(), percent = (n()/429))


URM_table

URM_table_int <- data %>% group_by(URM, opt_in) %>%
  summarise(var = "URM", n = n())


URM_table_int

##Transfer 
transfer_table <- data %>% group_by(transfer) %>%
  summarise(var = "transfer", n = n(), percent = (n()/429))


transfer_table

transfer_table_int <- data %>% group_by(transfer, opt_in) %>%
  summarise(var = "transfer", n = n())


transfer_table_int


##Gender

gender_table <- data %>% group_by(gender) %>%
  summarise(var = "gender", n = n(), percent = (n()/429))


gender_table

gender_table_int <- data %>% group_by(gender, opt_in) %>%
  summarise(var = "gender", n = n())


gender_table_int

## International table 
int_table <- data %>% group_by(int) %>%
  summarise(var = "International", n = n(), percent = (n()/429))


int_table

int_table_int <- data %>% group_by(int, opt_in) %>%
  summarise(var = "International", n = n())



grade_table <- data %>% group_by(opt_in) %>%
  summarise( mean(p_tot1, na.rm = T), mean(p_tot2, na.rm = T ), mean(p_tot3, na.rm = T), mean(p_tot4, na.rm = T), mean(p_tot5, na.rm = T) )




```



# Structural Equation Models 



```{r}

no_growth <- ('#latent structure
i =~ 1*p_tot1 + 1*p_tot2 + 1*p_tot3 + 1*p_tot4 + 1*p_tot5
'
)



```

#### Model 0: Fully Constrained no growth  ---Null model  

```{r}
fit0 <- growth(model = no_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.equal = c("residuals", "means", "lv.variances"), se = "robust")

fitMeasures(fit0)

parameterestimates(fit0)

```

##### Interpetation 
Baseline model, represents the null hypothesis assuming no change overtime and no differences between groups. 


#### Model 0.5 Intercepts only different 


```{r}
fit0_5 <- growth(model = no_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.equal = c("residuals", "lv.variances"), se = "robust")

fitMeasures(fit0_5)

parameterestimates(fit0_5)

anova(fit0, fit0_5)



```



### Linear Growth Models
Linear Model Structure: 
```{r}
lin_growth <- ('#latent structure
i =~ 1*p_tot1 + 1*p_tot2 + 1*p_tot3 + 1*p_tot4 + 1*p_tot5
s =~ 0*p_tot1 + 1*p_tot2 + 2*p_tot3 + 3*p_tot4 + 4*p_tot5')
```

#### Model 1: Linear growth but Fully Constrained in both groups ---ignoring the effect of opt-in

```{r}
lin_fit0 <- growth(model = lin_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.equal = c("residuals", "means", "lv.variances", "lv.covariances"), se = "robust")

fitMeasures(lin_fit0)

parameterEstimates(lin_fit0)

anova(fit0, lin_fit0)
```
### Interpretation 

Linear growth (no group differences) is not significantly better than Null model.In the 2024 data when we assume linear growth 

#### Model 2: free means in both groups  linear growth 
```{r}
lin_fit1 <- growth(model = lin_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.label = c("0", "1"), group.equal = c("residuals", "lv.covariances", "lv.variances"), se = "robust")

parameterEstimates(lin_fit1)

fitMeasures(lin_fit1)

anova(fit0, lin_fit1)

```



```{r}

lb_growth <- ('#latent structure
i =~ 1*p_tot1 + 1*p_tot2 + 1*p_tot3 + 1*p_tot4 + 1*p_tot5
s =~ 0*p_tot1 + NA*p_tot2 + 1*p_tot3 + NA*p_tot4 + NA*p_tot5')
```

#### Model 4: Fully constrained in both groups ---Non-linear model  

```{r}
lb_fit0 <- growth(model = lb_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.equal = c("residuals", "loadings", "means", "lv.variances", "lv.covariances"), se = "robust")

parameterEstimates(lb_fit0)

fitMeasures(lb_fit0)

anova(lb_fit0, lin_fit0) ###Latent basis is better than null 

```


#### Model 5 : Free loadings accept exam2 in both groups latent basis -- only allows post treament to vary by group -- post- trajectory only  different by groups -- Hypothesized Model 

```{r}

lb_growth_par <- ('#latent structure
i =~ 1*p_tot1 + 1*p_tot2 + 1*p_tot3 + 1*p_tot4 + 1*p_tot5
s =~ 0*p_tot1 + m*p_tot2 + 1*p_tot3 + NA*p_tot4 + NA*p_tot5')
```


```{r}
lb_fit1 <- growth(model = lb_growth_par, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.label = c("0", "1"),  group.equal = c("means", "residuals", "lv.variances", "lv.covariances"), se = "robust")


fitMeasures(lb_fit1)

parameterEstimates(lb_fit1)

anova(lb_fit1, lb_fit0) ##Lin_fit2 is better than lin_fit1

```


#### Model 6- free all loading to be different by group -- test the parallel trends Hypothesis
```{r}
lb_fit2 <- growth(model = lb_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.label = c("0", "1"), group.equal = c("means", "residuals", "lv.variances", "lv.covariances"), se = "robust")

parameterEstimates(lb_fit2)

fitMeasures(lb_fit2)

anova(lb_fit2, lb_fit1) 

```

##### Interpretation 

Model 6 did not fit better than model 5, meaning the parallel trends assumption holds:  no difference in loadings at time 2. 



#### Model 7 -- Under the assumption of parallel trends pre-intervention (which hold based on the SEM results) we  free the slope and intercepts by group 
```{r}
lb_fit3 <- growth(model = lb_growth_par, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.label = c("0", "1"), group.equal = c( "residuals", "lv.variances", "lv.covariances"), se = "robust")

parameterEstimates(lb_fit3)

fitMeasures(lb_fit3)

anova(lb_fit3, lb_fit1) 

```


#### Model 8: Are underlying differences between groups with the same trajectory enough to explain differences?-- alt explination
If 7 is not significantly better than 8 then that means all differences in performance can be attributed to underlying differences between groups 

```{r}
lb_fit4 <- growth(model = lb_growth, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.equal = c( "loadings", "residuals", "lv.variances", "lv.covariances"), se = "robust")

parameterEstimates(lb_fit4)

fitMeasures(lb_fit4)


anova(lb_fit3, lb_fit4)

```


```{r}

lb_growth2 <- ('#latent structure
i =~ 1*p_tot1 + 1*p_tot2 + 1*p_tot3 + 1*p_tot4 + 1*p_tot5
s =~ 0*p_tot1 + NA*p_tot2 + NA*p_tot3 + NA*p_tot4 + 1*p_tot5')
```

#### Model 4: Fully constrained in both groups ---Non-linear model  

```{r}
lb_fit5 <- growth(model = lb_growth2, data = data, estimator = "ML", missing = "fiml", group = "opt_in", group.label = c("0", "1"), group.equal = c("residuals", "means", "lv.variances", "lv.covariances"), se = "robust")

parameterEstimates(lb_fit5)

fitMeasures(lb_fit5)

anova(lb_fit1, lb_fit5) ###Latent basis is better than null 

```