---
title: "CleaningTestScript"
author: "Sydney Wood"
date: "2024-06-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load Packages 
```{r}
library(tidycode)
library(tibble)
library(dplyr)
library(tidyverse)
library(readr)
setwd("~/Documents/GitHub/MC_data_cleaning")
```


## Demographic Cleaning

```{r}
dem_data_raw <- read.csv(file = "Raw_dem_data_anon.csv")
dem_data_short <- dem_data_raw %>% select("anon_id", "consent", contains(".."))

colnames(dem_data_short) <- c("anon_id", "consent", "age", "year", "gender", "int_student", "esl", "e_exp", "e_lvl", "URM", "p_education", "m_education", "par_rel", "fin_support", "ses", "grant", "soc_med", "hw_time", "transfer")
```

## Change the categorical data to factors
```{r}
#dem_data<- dem_data_short %>% mutate_at(c(2,4,5,6,7, 10,13,14,15,16,19), factor) 
```

## consent
```{r}
dem_data_clean <- dem_data_short %>%
  mutate(consent = case_when(
    grepl("I do not consent", consent, fixed = TRUE) ~ 0,
    grepl("I consent to participate", consent, fixed = TRUE) ~ 1,
    TRUE ~ 0))



dem_data_clean <- dem_data_clean %>%
  filter(consent == 1)
```


## there is a 2002 in age column.
## age
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(age = case_when(
     grepl("2,002", age, fixed = TRUE) ~ "21",
    TRUE ~ age)) %>% mutate_at(3,as.numeric) 
```
## year
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(year = case_when(
    grepl("Freshman", year, fixed = TRUE) ~ 1,
    grepl("Sophomore", year, fixed = TRUE) ~ 2,
    grepl("Junior", year, fixed = TRUE) ~ 3,
    grepl("Senior - 4th year", year, fixed = TRUE) ~ 4,
    grepl("Senior - 5th+ year", year, fixed = TRUE) ~ 5,
    TRUE~NA
  )) %>% mutate_at(4,factor)
```

## Gender
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(gender = case_when(
    grepl("Woman", gender, fixed = TRUE) ~ 'Woman',
    grepl("Man", gender, fixed = TRUE) ~ 'Man',
    grepl("Non-binary or Genderqueer", gender, fixed = TRUE) ~ 'Other',
    TRUE~NA
  )) %>% mutate_at(5, factor)
```

## int_student
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(int_student = case_when(
    grepl("Yes", int_student, fixed = TRUE) ~ 1,
    grepl("No", int_student, fixed = TRUE) ~ 0,
    TRUE~NA
  )) %>% mutate_at(6, factor)
```

## esl
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(esl = case_when(
    grepl("English is my first language", esl, fixed = TRUE) ~ 1,
    grepl("English is not my first language", esl, fixed = TRUE) ~ 0,
    TRUE~NA
  ))%>% mutate_at(7, factor)
```

##e_exp
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(e_exp = str_remove_all(e_exp, "%")
  )%>% mutate_at(8, as.numeric)
```


## e_lvl
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(e_lvl = case_when(
    grepl("0", e_lvl, fixed = TRUE) ~ 0,
    grepl("1", e_lvl, fixed = TRUE) ~ 1,
    grepl("2", e_lvl, fixed = TRUE) ~ 2,
    grepl("3", e_lvl, fixed = TRUE) ~ 3,
    grepl("4", e_lvl, fixed = TRUE) ~ 4,
    grepl("5", e_lvl, fixed = TRUE) ~ 5, 
    grepl("6", e_lvl, fixed = TRUE) ~ 6, 
    TRUE~NA
  ))%>% mutate_at(9, as.integer)
```

### URM
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(URM = case_when(
    grepl("Black or African American", URM, fixed = TRUE) ~ 1,
    grepl("Caucasian", URM, fixed = TRUE) ~ 2, 
    grepl("East or South East Asian", URM, fixed = TRUE) ~ 3,
    grepl("Hispanic or Latino", URM, fixed = TRUE) ~ 4,
    grepl("Middle Eastern or West Asian", URM, fixed = TRUE) ~ 5,
    grepl("Mixed Race", URM, fixed = TRUE) ~ 6,
    grepl("North or Central Asian",URM, fixed = TRUE) ~ 7,
    grepl("Pacific Islander", URM, fixed = TRUE) ~ 8,
    grepl("South Asian", URM, fixed = TRUE) ~ 9,
    TRUE~NA
  ))%>% mutate_at(10, factor)
```

### p_education
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(p_education = case_when(
    grepl("He never attended school", p_education, fixed = TRUE) ~ 1,
    grepl("He left when he graduated from high school (or GED)", p_education, fixed = TRUE) ~ 2, 
    grepl("He left school before he graduated from high school", p_education, fixed = TRUE) ~ 3,
    grepl("He attended some college, but left before he earned a 4-year degree", p_education, fixed = TRUE) ~ 4,
    grepl("He earned a 4-year degree", p_education, fixed = TRUE) ~ 5,
    grepl("He earned a graduate degree (Masters or Ph.D)", p_education, fixed = TRUE) ~ 6,
    TRUE~NA
  ))
```


### m_education
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(m_education = case_when(
    grepl("She never attended school", m_education, fixed = TRUE) ~ 1,
    grepl("She left when she graduated from high school (or GED)", m_education, fixed = TRUE) ~ 2, 
    grepl("She left school before she graduated from high school", m_education, fixed = TRUE) ~ 3,
    grepl("She attended some college, but left before she earned a 4-year degree", m_education, fixed = TRUE) ~ 4,
    grepl("She earned a 4-year degree", m_education, fixed = TRUE) ~ 5,
    grepl("She earned a graduate degree (Masters or Ph.D)", m_education, fixed = TRUE) ~ 6,
    TRUE~NA
  ))
```

##Get a new column first_gen by p_education and m_education
```{r}
dem_data_clean <- dem_data_clean %>% mutate(first_gen = case_when(p_education < 5 & m_education < 5 ~ 1, p_education >= 4 | m_education >= 4 ~ 0))

dem_data_clean <- dem_data_clean %>%  mutate(first_gen = case_when(first_gen == NA & p_education < 5 | m_education < 5 ~ 1, .default = first_gen)) %>% mutate( first_gen = case_when(first_gen == NA & m_education < 5 | p_education < 5 ~ 1, .default = first_gen)) %>% mutate_at(20, factor)
```

## par_rel
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(par_rel = case_when(
    grepl("Together", par_rel, fixed = TRUE) ~ "Together",
    grepl("Divorced", par_rel, fixed = TRUE) ~ "Divorced",
    grepl("Separated", par_rel, fixed = TRUE) ~ "Separated",
    grepl("Single", par_rel, fixed = TRUE) ~ "Single",
    TRUE~NA
  ))
```

##fin_support
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(fin_support = case_when(
    grepl("No support", fin_support, fixed = TRUE) ~ 1,
    grepl("Very little support", fin_support, fixed = TRUE) ~ 2,
    grepl("A little support",fin_support, fixed = TRUE) ~ 3,
    grepl("Some support", fin_support, fixed = TRUE) ~ 4,
    grepl("Halfway supported", fin_support, fixed = TRUE) ~ 5, 
    grepl("Mostly supported", fin_support, fixed = TRUE) ~ 6, 
    grepl("Fully supported", fin_support, fixed = TRUE) ~ 7,
    TRUE~NA
  ))
```

## ses
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(ses = case_when(
    grepl("I did not qualify for 'free or reduced cost lunch' at all in high school", ses, fixed = TRUE) ~ 0,
    grepl("I don't know if I qualified for a 'free or reduced cost lunch' program", ses, fixed = TRUE) ~ 1,
    grepl("I qualified for 'free or reduced cost lunch' for all or most of high school",ses, fixed = TRUE) ~ 2,
    grepl("I qualified for 'free or reduced cost lunch' for some of high school", ses, fixed = TRUE) ~ 3,
    TRUE~NA
  ))%>% mutate_at(15, factor)
```

## grant
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(grant = case_when(
    grepl("I do not qualify for a Pell Grant", grant, fixed = TRUE) ~ 0,
    grepl("I do qualify for a Pell Grant", grant, fixed = TRUE) ~ 1,
    grepl("I don't know if I qualify for a Pell Grant",grant, fixed = TRUE) ~ 2,
    TRUE~NA
  ))%>% mutate_at(16, factor)
```

## soc_med
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(soc_med = case_when(
    soc_med == 0 ~ NA, .default = soc_med
    ))%>%mutate(soc_med = str_remove_all(soc_med, ",")
  )%>% mutate_at(17, as.numeric)
```

## hw_time
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(hw_time = case_when(
    hw_time == 0 ~ NA, .default = hw_time
    ))%>% mutate(hw_time = str_remove_all(hw_time, ",")
  )%>% mutate_at(18, as.numeric)
```



## transfer
```{r}
dem_data_clean <- dem_data_clean %>%
  mutate(transfer = case_when(
    grepl("Yes", transfer, fixed = TRUE) ~ 1,
    grepl("No", transfer, fixed = TRUE) ~ 0,
    TRUE~NA
  ))%>% mutate_at(19, factor)
```



# save csv 
```{r}
write.csv(dem_data_clean, file = "First_dataset.csv", row.names = F)
```



## Overall Grade Data (canvas)

```{r}
cleaned <- read.csv(file = "wq_grade_data_cleaned_anon.csv")

raw <-  read.csv(file = "wq23_canvas_data_raw_anon.csv")

```


P+P (prep & Participation) --- Final score cannot be above 250 


There are 6 exams, but only 5 count toward the final grade. The "exam_total" the sum of  the 5 highest grades of the "exam" category turned in to a percentage (out of 750). 


while calculating the final column you will have columns for all the raw exam and raw_final_grade, but at the very end you will drop those 


For exams:  Turn each exam to % correct (all exams are out of 150) 


Extra Credit: Final Points & Exam.Correction... 

P+P - Final Points 


final grade calculation = p+p_final(upto 250) + raw_exam_total(upto 750, not percent, but only included the 5 highest exam grades) + extra_credit_total


After calculating turn final grade into % by divide by 1000 and then * 100 

### Canvas
```{r}
wq_grades <- read.csv(file = "wq23_canvas_data_raw_anon.csv")
wq_grades_short <- wq_grades %>% select("anon_id", "Exam.1..965996.", "Exam.2..965997.", "Exam.3..965998.", "Exam.4..965999.", "Exam.5..966000.", "Final.Exam..966002.", "Prep.Participation..up.to.250.points..Final.Points", "Extra.Credit.Final.Points", "Exam.Corrections...966001." ) %>% mutate_at(-c(1,2), as.numeric)

colnames(wq_grades_short) <- c("anon_id", "exam1", "exam2","exam3","exam4","exam5","exam6", "prep_p_raw", "extra_credit", "e_correct")

```

##p_p_final
```{r}
wq_grades_short$p_p_final <- wq_grades_short$prep_p_raw
wq_grades_short$p_p_final[wq_grades_short$prep_p_raw >= 250] <- 250
```


#drop the lowst exam score
```{r}
wq_exams <- wq_grades_short %>% select(contains("exam"))
wq_exams$lowest <- apply(wq_exams, 1, min)
wq_exams$lowest <- wq_exams$lowest * -1
wq_grades_short$exam_total <- apply(wq_exams, 1, sum)
```


```{r}
final_grade_calc <- wq_grades_short %>% select("extra_credit", "p_p_final", "exam_total")
wq_grades_clean <- wq_grades_short %>% 
  mutate(final_grade = apply(final_grade_calc, 1, sum)) %>%
  mutate(opt_in = case_when(e_correct == 0 ~ 0, e_correct > 0 ~ 1)) 
```

```{r}
wq_grades_clean <- wq_grades_clean %>% mutate_at(c(2:8),~na_if(.,0) )
exam_col <- wq_grades_clean %>% select(contains("exam"), -exam_total)
```

```{r}
div <- function(x) ((x/150) *100)

wq_grades_final <- wq_grades_clean %>% mutate_at(colnames(exam_col), div) %>% mutate(exam_total = (exam_total/750)*100) %>% mutate(final_grade = (final_grade/1000)*100)
```

#save file
```{r}
write.csv(wq_grades_final, file = "wq_grades_final.csv", row.names = F)
```




## 

# Full Data 


## Combine Dem & Grades
```{r}
grades <- read.csv(file ="wq_grades_final.csv")

dem <- read.csv("First_dataset.csv")

full_grades <- grades %>% select(-"anon_id")

full_data <- full_join(dem,grades, by = "anon_id")

full_data <- full_data %>% filter(!is.na(consent))

full_data <- full_data %>% select(-"consent")
```


```{r}
setwd("/~/GitHub/MC_data_cleaning/Raw Exam Data")


exam1A <- read.csv("~/GitHub/MC_data_cleaning/Raw Exam Data/1_A_Mar23_anon.csv")



exam1A <- exam1A %>% filter(Status == "Graded") %>% select(1:11)
exam1B <- exam1B %>% filter(Status == "Graded") %>% select(1:11)


e1Agrade
e1Bgrade
e1Cgrade
e1Dgrade

write.csv()

exam1_full <- rbind(exam1A, exam1B)

```

Exam 1:

H1_nondirectional == h2 
claim.type.explain == claim_ex
Mill's.Criteria == temp
Alternate.Explination == alt.exp


## Get only the written score 


```{r}
setwd("~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam1")
exam1A <- read.csv("1_A_Mar23_anon.csv")
```


```{r}
setwd("~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam1")
w_exam1D<- read.csv("1_D_Mar23_anon.csv") #I manually changed the file name for each exam

w_exam1D <- w_exam1D %>% select("anon_id","View.Count", "Status", 15, 17, 18, 20, 24, 29, 30, 31, 32) #these change for each exam as well 
  
q_names <- c("anon_id", "views", "Status", "h0", "h1", "h2", "pv_op", "ov_op", "claim_ex", "temp", "alt_ex","interpret")

colnames(w_exam1D) <- q_names

w_exam1D <- w_exam1D %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A")
```

#w_exam1B <- w_exam1B %>% select("anon_id","View Count", 15, 17, 18, 20, 24, 29, 30, 31, 32)
#w_exam1C <- w_exam1C %>% select("anon_id","View Count", 15, 17, 18, 20, 24, 29, 30, 31, 32)
#w_exam1D <- w_exam1D %>% select("anon_id","View Count", 15, 17, 18, 20, 24, 29, 30, 31, 32)

##Combine the results
```{r}
w_exam1_full <- rbind(w_exam1A, w_exam1B, w_exam1C, w_exam1D)

w_exam1_full <- w_exam1_full %>% filter(anon_id != "dropped")

```

## write the file
```{r}
write.csv(w_exam1_full, file = "exam1_writtenQs.csv")
```


## Exam 1 Loop
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam1"
Exam1 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)

```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam1) {
  # Read the CSV file
  exam1 <- read.csv(file)
  
  # Select the required columns
  exam1 <- exam1 %>% 
    select("anon_id", "View.Count", "Status", 15, 17, 18, 20, 24, 29, 30, 31, 32)
  
  # Rename the columns
  q_names <- c("anon_id", "views1", "Status", "h0", "h1", "h2", "pv_op", "ov_op", "claim_ex", "temp", "alt_ex","interpret")
  colnames(exam1) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam1 <- exam1 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A") %>% filter(anon_id != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam1
}

# Combine all results into a single data frame
Exam1_full <- bind_rows(results_list, .id = "source")


```


## write the file
```{r}
write.csv(Exam1_full, file = "exam1_writtenQs.csv", row.names = F)
```



## Exam 2 Loop 
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam2"
Exam2 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)

```

```{r}
# Create an empty list to store the results
results_list2 <- list()
```

```{r}
# Iterate over each file
for (file in Exam2) {
  # Read the CSV file
  exam2 <- read.csv(file)
  
  # Select the required columns
  exam2 <- exam2 %>% 
    select("anon_id", "View.Count", "Status", 15,contains("floater"), 20, contains("Construct.Validity"), 24, 26, contains("Interpretation"))
  
  # Rename the columns
  q_names <- c("anon_id", "views2", "Status", "pv_op", "cv_float", "ov_op", "cv", "reliability", "h1", "interpret")
  colnames(exam2) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam2 <- exam2 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A") %>% filter(anon_id != "dropped")
  
  # Add the processed data to the results list
  results_list2[[basename(file)]] <- exam2
}

# Combine all results into a single data frame
final_result2 <- bind_rows(results_list2, .id = "source")

## write file
write.csv(final_result2, file = "exam2_writtenQs.csv", row.names = F)
```

## Exam 3 Loop 
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam3"
Exam3 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
# Create an empty list to store the results
results_list3 <- list()
```

```{r}
# Iterate over each file
for (file in Exam3) {
  # Read the CSV file
  exam3 <- read.csv(file)
  
  ## Turn the files to character
   exam3$anon_id <- as.character(exam3$anon_id)
  
  # Select the required columns
  exam3 <- exam3 %>% 
    select("anon_id", "View.Count", "Status",15, 19, 23, 24, 25, contains("Confound"), 29, contains("Interpretation"))
  
  # Rename the columns
  q_names <- c("anon_id", "views3", "Status", "pv_op", "cv", "compare_cv", "internal1", "internal2", "confound", "design_ex", "interpret")
  colnames(exam3) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam3 <- exam3 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A") %>% filter(anon_id != "dropped")
  
  # Add the processed data to the results list
  results_list3[[basename(file)]] <- exam3
}

# Combine all results into a single data frame
final_result3 <- bind_rows(results_list3, .id = "source")

## write file
write.csv(final_result3, file = "exam3_writtenQs.csv", row.names = F)
```

## Exam 4 Loop 
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam4"
Exam4 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)

```

```{r}
# Create an empty list to store the results
results_list4 <- list()
```

```{r}
# Iterate over each file
for (file in Exam4) {
  # Read the CSV file
  exam4 <- read.csv(file)
  
  # Select the required columns
  exam4 <- exam4 %>% 
    select("anon_id", "View.Count", "Status", 20, 21, 24, 25, 26, 27, 33, 34, 35)
  
  # Rename the columns
  q_names <- c("anon_id", "views4", "Status", "new_claim", "ov_op", "cv", "internal", "confound", "fix_confound", "sampling", "external", "replication")
  colnames(exam4) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam4 <- exam4 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A") %>% filter(anon_id != "dropped")
  
  # Add the processed data to the results list
  results_list4[[basename(file)]] <- exam4
}

# Combine all results into a single data frame
final_result4 <- bind_rows(results_list4, .id = "source")

## write file
write.csv(final_result4, file = "exam4_writtenQs.csv", row.names = F)
```




## Exam 5 Loop 
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/Raw Exam Data/Exam5"
Exam5 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)

```

```{r}
# Create an empty list to store the results
results_list5 <- list()
```

```{r}
# Iterate over each file
for (file in Exam5) {
  # Read the CSV file
  exam5 <- read.csv(file)
  
  # Select the required columns
  exam5 <- exam5 %>% 
    select("anon_id", "View.Count", "Status", 15, 20, 24, 25, 26, 30, 31, 32)
  
  # Rename the columns
  q_names <- c("anon_id", "views5", "Status", "pv_op", "cv", "cv_compare", "confound", "internal", "interpret", "external", "replication")
  colnames(exam5) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam5 <- exam5 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(anon_id != "#N/A") %>% filter(anon_id != "dropped")
  
  # Add the processed data to the results list
  results_list5[[basename(file)]] <- exam5
}

# Combine all results into a single data frame
final_result5 <- bind_rows(results_list5, .id = "source")

## write file
write.csv(final_result5, file = "exam5_writtenQs.csv", row.names = F)
```








## Combine Dem & Grades
```{r}
grades <- read.csv(file ="wq_grades_final.csv")

dem <- read.csv("First_dataset.csv")

full_grades <- grades %>% select(-"anon_id")

full_data <- full_join(dem,grades, by = "anon_id")

full_data <- full_data %>% filter(!is.na(consent))

full_data <- full_data %>% select(-"consent")
```


# create p_tot (percent accuracy of just the written portion of the exam )

## p_tot1
```{r}
library(dplyr)
exam1_short <- read.csv("exam1_writtenQs.csv", sep = ",")
```

```{r}
exam1_calc <- exam1_short %>% select(4:12)
exam1_short <- exam1_short %>%
  mutate(written = rowSums(exam1_calc, na.rm = TRUE))
```

```{r}
exam1_final <- exam1_short %>% mutate(p_tot1 = (written/75)*100) 
```

```{r}
exam1_end <- exam1_final %>% select("anon_id", "views1", "p_tot1")
```

```{r}
full_data <- left_join(full_data, exam1_end, by = "anon_id" )
```



##p_tot2
```{r}
library(dplyr)
exam2_short <- read.csv("exam2_writtenQs.csv", sep = ",")
```

```{r}
exam2_calc <- exam2_short %>% select(4:10)
exam2_short <- exam2_short %>%
  mutate(written = rowSums(exam2_calc, na.rm = TRUE))
```

```{r}
exam2_final <- exam2_short %>% mutate(p_tot2 = (written/85)*100) 
```

```{r}
exam2_end <- exam2_final %>% select("anon_id", "views2", "p_tot2")
```

```{r}
full_data <- left_join(full_data, exam2_end, by = "anon_id" )
```

## p_tot3
```{r}
library(dplyr)
exam3_short <- read.csv("exam3_writtenQs.csv", sep = ",")
```

```{r}
exam3_calc <- exam3_short %>% select(4:11)
exam3_short <- exam3_short %>%
  mutate(written = rowSums(exam3_calc, na.rm = TRUE))
```

```{r}
exam3_final <- exam3_short %>% mutate(p_tot3 = (written/80)*100) 
```

```{r}
exam3_end <- exam3_final %>% select("anon_id", "views3", "p_tot3")
```

```{r}
full_data <- left_join(full_data, exam3_end, by = "anon_id" )
```


## p_tot4
```{r}
library(dplyr)
exam4_short <- read.csv("exam4_writtenQs.csv", sep = ",")
```

```{r}
exam4_calc <- exam4_short %>% select(4:12)
exam4_short <- exam4_short %>%
  mutate(written = rowSums(exam4_calc, na.rm = TRUE))
```

```{r}
exam4_final <- exam4_short %>% mutate(p_tot4 = (written/85)*100) 
```

```{r}
exam4_end <- exam4_final %>% select("anon_id", "views4", "p_tot4")
```

```{r}
full_data <- left_join(full_data, exam4_end, by = "anon_id" )
```



## p_tot5
```{r}
library(dplyr)
exam5_short <- read.csv("exam5_writtenQs.csv", sep = ",")
```

```{r}
exam5_calc <- exam5_short %>% select(4:11)
exam5_short <- exam5_short %>%
  mutate(written = rowSums(exam5_calc, na.rm = TRUE))
```

```{r}
exam5_final <- exam5_short %>% mutate(p_tot5 = (written/80)*100) 
```

```{r}
exam5_end <- exam5_final %>% select("anon_id", "views5", "p_tot5")
```

```{r}
full_data <- left_join(full_data, exam5_end, by = "anon_id" )
```




You'll end with a dataset: 

exam1_short <- anon_id, views, p_tot1


full_data <- left_join(full_data, exam1_short, by = anon_id )
