---
title: "Lab4"
author: "Jane He and Monica Orme"
date: last-modified
format: 
  html:
    toc: true
    toc-float: true
    df-print: tibble
    code-copy: true
    code-line-numbers: true
    code-link: true
    preview-links: true
    self-contained: true
    fig-height: 4
    fig-width: 6
    fig-align: center
    html-math-method: mathml
    output-file: Lab4_Supplementary_Page.html
    format-links: true
  revealjs: 
    incremental: true
    code-tools: true
    code-copy: true
    code-line-numbers: true
    code-link: true
    preview-links: true
    slide-level: 4
    slide-number: true
    self-contained: true
    fig-height: 4
    fig-width: 6
    fig-align: center
    margin-left: "0"
    margin-right: "0"
    width: 1400
    footer: "PSC103A WQ24"
    output-file: Lab4_Supplementary_Slides.html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Goals for Today

-   Clarifying Questions from Lab 3
-   R Skills Recap
-   Subset Data Frame
-   Common Error Messages
-   Course Project Overview
-   Practice with Course Dataset

<!-- Section for reading in files - not visible to students -->

<!--# Comment out the other person's path when rendering the qmd -->

```{r, include=FALSE}
# A01 path 
#bmi_data_csv <- read.csv(file = "/Users/jane/Documents/GitHub/PSC103A/Data/Example/lab2data.csv", header = TRUE,  stringsAsFactors = TRUE)

# A02 path
bmi_data_csv <- read.csv(file = "C:\\Users\\Monica\\OneDrive\\st - PSC 103A\\Discussions-Labs\\Data\\lab2data.csv", header = TRUE,stringsAsFactors = TRUE)
```

<!-- created a vector for MIDUS3 subset to replace the long variable list -->

```{r allowedVariables, eval=TRUE, echo=FALSE}
allowed_var <- c("M2ID",
                 "SAMPLMAJ",
                 "C1PRAGE",
                 "C1PRSEX",
                 "C1PA1",
                 "C1PA2",
                 "C1PA3",
                 "C1PA39",
                 "C1PA59",
                 "C1PDEPAF",
                 "C1PANHED",
                 "C1PDEPRE",
                 "C1PANXIE",
                 "C1PPANIC",
                 "C1PPARTN",
                 "C1PB32A",
                 "C1PD1",
                 "C1PF1",
                 "C1PF12A",
                 "C1SSATIS2",
                 "C1SHLOCS",
                 "C1SAMPLI",
                 "C1SA15",
                 "C1SNEGAF",
                 "C1SNEGPA",
                 "C1SPOSAF",
                 "C1SPOSPA",
                 "C1SBADL2",
                 "C1SIADL",
                 "C1SINTAG",
                 "C1SWSTHI",
                 "C1SBMI",
                 "C1SPWBA1",
                 "C1SPWBE1",
                 "C1SPWBG1",
                 "C1SPWBR1",
                 "C1SPWBU1",
                 "C1SPWBS1",
                 "C1SPWBA2",
                 "C1SPWBE2",
                 "C1SPWBG2",
                 "C1SPWBR2",
                 "C1SPWBU2",
                 "C1SPWBS2",
                 "C1SMPQWB",
                 "C1SMPQSP",
                 "C1SMPQAC",
                 "C1SMPQSC",
                 "C1SMPQSR",
                 "C1SMPQAG",
                 "C1SMPQAL",
                 "C1SMPQCN",
                 "C1SMPQTR",
                 "C1SMPQHA",
                 "C1SOPTIM",
                 "C1SPESSI",
                 "C1SREINT",
                 "C1SACTIV",
                 "C1SPLAN",
                 "C1SVENT",
                 "C1SDENIA",
                 "C1SDISEN",
                 "C1SPRCOP",
                 "C1SEMCOP",
                 "C1SSWBSI",
                 "C1SSWBAO",
                 "C1SSWBSC",
                 "C1SSWBSA",
                 "C1SSYMP",
                 "C1SMNDFU",
                 "C1SLFEDI",
                 "C1SP3",
                 "C1SP4A",
                 "C1SP4B",
                 "C1SP4C",
                 "C1SP4D",
                 "C1SP4E",
                 "C1SP4F",
                 "C1SP4G",
                 "C1SP4H",
                 "C1SP4I",
                 "C1SP4J",
                 "C1SP4K",
                 "C1SP4L",
                 "C1SQ1",
                 "C1SQ4",
                 "C1PA25BS")
```

<!-- switch TRUE/FALSE for eval only. all other options can remain. -->

```{r, eval=F, echo=F,include=F}
load("/Users/jane/Documents/GitHub/PSC103A/Data/MIDUS3/36346-0001-Data.rda")
midus3_raw <- da36346.0001
midus3_subset <- da36346.0001[, allowed_var] 
midus3_clean <- midus3_subset[midus3_subset$SAMPLMAJ %in% c("(01) MAIN RDD", "(04) CITY OVERSAMPLE" ), ]  
psc103Adata <- midus3_clean
```

```{r, eval=T, echo=F,include=F}
setwd("C:\\Users\\Monica\\OneDrive\\st - PSC 103A\\Discussions-Labs\\Data\\ICPSR_36346\\DS0001")
load(file='36346-0001-Data.rda')
tempdata <- da36346.0001[, allowed_var] 
psc103Adata <- tempdata[tempdata$SAMPLMAJ %in% c("(01) MAIN RDD", "(04) CITY OVERSAMPLE" ), ]  
```

<!--# Lab Material Starts -->

# R Skills Recap

Let's recap on some concepts and functions covered in the previous weeks 👀

## Finding Information from Datasets {.smaller}

Before we analyze data, it is important that we first have a good understanding of its properties. Some questions that we should ask ourselves to better understand the properties of a particular dataset before conducting any data analysis include:

::: columns
::: {.column width="50%"}
-   What is the sample size (*n*)?

<!-- -->

-   What are the data types of the datasets' variables?

    -   For categorical variables, how many categories does each variable have?

-   Are there any missing values?
:::

::: {.column width="50%"}
-   What are the descriptive statistics of the variables?

    -   For categorical variables:

        -   what are the relative frequencies of the categorical variables?

    -   For numeric variables:

        -   What is the center?

        -   What is the spread (variability)?
:::
:::

::: fragment
Let's review together how we can answer these questions using R code!
:::

### Sample Size and Data Types {.smaller}

-   **Sample size** (*n*) refers to the number of individuals or objects in the sample

-   **Data types** refer to a type of value that a variable has

    -   **Categorical variables in R** should be stored as [**factor**]{.underline} **values** in your dataframe

    -   **Numerical variables in R** should be stored as [**numeric**]{.underline} **or [integer]{.underline} values** in your dataframe

-   **Dataframes** refer to objects in R that we save as a result of importing a dataset using either `read.csv()` for csv files or `read.table()` for text files

    -   Each row corresponds to an observation and each column corresponds to a variable

-   In R, we can find the sample size and data types of each variable from a dataset in a few ways:

    1.  Input the dataframe into the `str()` function

        -   Find the sample size from the number of observations that are listed in the first row from the output
        -   The data types in R are shown next to each variable

    2.  Input the dataframe into the `describe()` function from the `Hmisc` package

        -   Find the sample size as the number of observations that are listed in the line below the dataframe name

#### Example 1: n and Data Types {.smaller}

Method 1: Using the `str()` function

::: columns
::: {.column width="45%"}
-   Method 1:

    ```{r}
    # Check the sample size
    # and data types
    # using str()

    str(bmi_data_csv)
    ```
:::

::: columns
::: {.column width="5%"}
<!-- empty space -->
:::
:::

::: {.column width="45%"}
-   The sample size is n = 232

    -   This can be found in the first line of the output ” ‘data.frame’: 232 obs. of 5 variables ”

-   The `biosex` variable is a variable with 2 levels "FEMALE" and "MALE"

    -   This can be found in the second line of the output ” Factor w/ 2 levels “FEMALE”,“MALE” ”

    -   The other data types can be checked similarly in the remaining lines of the output
:::
:::

#### Example 2: n and Data Types {.smaller}

::: columns
::: {.column width="60%"}
-   Method 2: Using the `describe()` function

    ```{r}
    # Check the sample size and data types using Hmisc::describe()  
    library(Hmisc)
    # use :: to avoid package conflict if psych package is also loaded
    Hmisc::describe(bmi_data_csv)
    ```
:::

::: {.column width="40%"}
-   n = 232 can be found in the line below the dataframe name in " 5 Variables 232 Observations "

-   The `biosex` variable is a factor with 2 levels "FEMALE" and "MALE"

    -   This can be found in the second section of the output

    -   Note that the count under "distinct" is small and frequencies of each category are provided, which the Hmisc package only provides for factor variables

-   The other data types can be checked similarly in the remaining lines of the output.
:::
:::

### Checking for Missing Values {.smaller}

In psychological studies, some participants might drop out or skip answering certain questions. This leads to some values being missing in a dataset.

-   It is important that we **check for missing values early** on to have a **more accurate understanding of our data** and to **ensure** that the **descriptive statistics are correctly calculated**

-   Options for checking missing values in R:

    1.  Input the dataframe into the `summary()` function

        -   Look for "`NA`'s" in each variable
        -   There will be count displayed next to "NA: " for the variables that contain missing values

    2.  Input the dataframe into the `describe()` function from the `Hmisc` package

        -   In the output, check the column that says "missing"

#### Example 1: Check NA {.smaller}

-   Method 1: Using the `summary()` function from base R

    ```{r}
    # Check the missing values using summary()
    summary(bmi_data_csv)
    ```

\n

-   The variables `height_in`, `weight_lbs`, and `age_yr` all contain missing values
    -   Note that the counts that are displayed next to "NA's" for each variable that contains missing values
-   In contrast, the variables `biosex` and `ed_cmplt` do not contain any missing values
    -   There are no "NA's" displayed

#### Example 2: Check NA {.smaller}

::: columns
::: {.column width="60%"}
-   Method 2:

    ```{r}
    # Check the missing values using Hmisc::describe()  
    library(Hmisc)
    # use :: to avoid package conflict if psych package is also loaded
    Hmisc::describe(bmi_data_csv)
    ```
:::

::: {.column width="40%"}
-   The variables `height_in`, `weight_lbs`, and `age_yr` all contain missing values

    -   Note that the counts displayed under the "missing" section for these variables are greater than 0

-   In contrast, the variables `biosex` and `ed_cmplt` do not contain any missing values

    -   Counts displayed under the "missing" section are exactly 0

    <!-- The n being displayed for them are also equal to the sample size of data frame -->
:::
:::

### Descriptive Statistics: Categorical Variables {style="font-size: 90%"}

The relative frequency is a common descriptive statistic for categorical variables

-   These can be created in R using the `table()` function to produce the frequencies then dividing the frequencies by the total number of observations

-   If there are missing values, we need to adjust the denominator to account for the number of missing values in the variable that we are calculating the relative frequency of

-   We can adjust the relative frequency calculation for missing values as:

    -   **Relative Frequency =** $\frac{\textbf{frequency}}{\textbf{n - (# of missing observations in the variable)}}$

        ::: nonincremental
        -   where n refers to # of observations in the dataset
        :::

#### Example: Categorical Variables {.smaller}

-   An example in R:

    ```{r}
    #| output-location: fragment

    # calculate frequencies to create a frequency table
    smokers_freq = table(psc103Adata$C1PA39) 

    # count the number of missing values in variable C1PA39
    count_miss_smoker = sum(is.na(psc103Adata$C1PA39)) 

    # adjust denominator for the number of missing values
    complete_smokers= (length(psc103Adata$C1PA39) - count_miss_smoker)

    # Find relative frequencies after accounting for the number of missing values
    smokers_relfreq = smokers_freq/complete_smokers
    smokers_relfreq
    ```

<!-- -->

-   The function `sum(is.na())` will count the number of missing values for a variable

-   The function `length()` counts the total number of rows in the dataframe, regardless of missingness. 

### Descriptive Statistics for Numeric Variables {.smaller}

Descriptive statistics for datasets can be readily calculated using functions from Base R.

::: columns
::: {.column width="55%"}
-   Central Measures

    -   Mean - `mean()`

    -   Median - `median()`

    -   Trimmed Mean - `mean(..., trim = ...)`

    -   Specify the % of data to trim in the `trim` argument

        -   E.g. the `trim` argument for a 10% trimmed mean is `trim = 0.1`
:::

::: {.column width="5%"}
<!-- empty space -->
:::

::: {.column width="40%"}
-   Variability Measures

    -   Variance - `var()`

    -   Standard Deviation - `sd()`

    -   Range - `range()`

    -   Interquartile Range - `IQR()`
:::
:::

-   Datasets may contain missing values. Again, check if they are in your dataset using the `summary()` function from Base R or the `describe()` function from the `Hmisc` package.

-   If missing values exist within a variable, remove the missing values before calculating each descriptive statistic using the option **`na.rm=TRUE`**. (Recall that R denotes missing values as `NA`).

#### Example: Numeric Variables {.smaller}

::: columns
::: {.column width="40%"}
-   Central Measures

    -   Example:

        ```{r}
        # measures of central tendency 
        mean_height <- mean(bmi_data_csv$height_in, 
        na.rm=TRUE)   
        median_height <- median(bmi_data_csv$height_in, 
        na.rm=TRUE)  
        trimm_mean_height <- mean(bmi_data_csv$height_in, 
                                  trim = .10, na.rm = TRUE)

        # displaying central measures 
        mean_height 
        median_height 
        trimm_mean_height
        ```
:::

::: {.column width="10%"}
:::

::: {.column width="40%"}
-   Variability Measures

    -   Example:

        ```{r}
        # measures of variability 
        range_age <- range(bmi_data_csv$age_yr, na.rm = TRUE) 
        variance_age <- var(bmi_data_csv$age_yr, na.rm = TRUE) 
        sd_age <- sd(bmi_data_csv$age_yr, na.rm = TRUE) 
        iqr_age <- IQR(bmi_data_csv$age_yr, na.rm = TRUE)

        # displaying variability measures 
        range_age
        variance_age 
        sd_age 
        iqr_age
        ```
:::
:::

## Bonus Tip: Rounding Calculations in R

When reporting descriptive statistics in reports and papers, we often only need the first few decimal places (e.g. 2 decimal places).

-   We can round our descriptive statistics to a certain number of decimal places using the `round()` function from base R

    -   Here is an example:

        ```{r}
        # round relative frequencies to 2 decimal places
        # specify the "digits" argument to get desired decimal places 
        round(smokers_relfreq, digits = 2)
        ```

# Subsetting Data

When analyzing data, some of the questions of interest may be focused on a smaller portion of your data. We can extract a smaller portion of data by subsetting in R.

### Subsetting Dataframes {.smaller}

Recall that dataframes consist of rows (stores each observation/participant) and columns (stores each variable).\
An operator that can be used to subset data is the `[]` operator.\
For a data frame named `df` the general format to subset is `df[rows, columms]`

::: columns
::: {.column width="45%"}
-   For the `rows` parameter, pass either:

    -   the row names of the selected rows

    -   the index/indices as a single value or a vector of values

        -   **Indexing in R starts at 1**

            -   E.g. subset the first row: `df[1,]`

    -   a logical statement that, when evaluated, reduces to the row indices
:::

::: {.column width="10%"}
:::

::: {.column width="45%"}
-   For the `columms` parameter, pass either:

    -   the column index/indices of the selected columns as a vector of values or logical operators

        -   **Indexing in R starts at 1**

            -   E.g. subset the first 3 columns: `df[,1:3]`

    -   a vector of variable names that reduces to the column indices
:::
:::

-   If subsetting is done by only rows or only columns, then leave the other value blank

    -   For example, to subset the `df` data frame only by rows, the general form reduces to `df[rows,]`. Similarly, to subset only by columns, `df[,cols]`

### Steps to Subset Dataframes in R: {.smaller}

1.  Based on the question of interest, determine the relevant variables in R and which of those values are applicable
2.  Subset the dataframe using the `[]` operator and `which()` command with logical operators. Then, **store it as a new object**
    -   Refresh: Some logical operators in R include: \<,\<=, \>, \>=, ==, !=. Go back to learning module 1 and/or the Lab 1 supplementary materials from the announcement to review these.

<!-- -->

3.  Check that the dataframe was subset correctly using the `summary()` command

### Example: Subsetting Dataframes {.smaller}

-   Example: Create a new dataframe of [males]{.underline} that are [older than 25]{.underline} years old. Generate descriptive statistics for the weight of the participants in that group.

    -   Check the variables of interest

        ```{r}
        # review the dataset's
        # properties
        str(bmi_data_csv)
        ```

        -   We can subset the data based on the `biosex` and `age_yr` variables.

### Example: Subsetting Dataframes (continued) {.smaller}

::: columns
::: {.column width="45%"}
-   Subset the data into a dataframe object that contains [males]{.underline} that are [older than 25]{.underline} years old.

    ```{r, eval=T}
    # subset the data by rows with logical operataors 
    MALE_older <- bmi_data_csv[which(bmi_data_csv$biosex=='MALE'
                                     & bmi_data_csv$age_yr > 25),]
    # note the position of the comma
                                 
    # check the subsetting
    summary(MALE_older)
    ```
:::

::: {.column width="5%"}
<!--  -->
:::

::: {.column width="45%"}
-   When creating the `MALE_older` dataframe we told R, to **only keep** participants that are both male and older than 25 years old.

-   The `which()` command extracts the row indices that satisfy the logical condition(s) that are specified inside of the function

-   The logical conditions here are `bmi_data_csv$biosex=='MALE' & bmi_data_csv$age_yr > 25`

-   Include the comma "`,`" before the ending bracket to subset the participants that satisfy the criteria

    -   Recall that in most dataframes, the participants' information is stored in the rows.
:::
:::

### Example: Subsetting Dataframes (continued) {.smaller}

-   Generate the descriptive statistics for weight on the subsetted dataframe

    ```{r}
    # obtain descriptives for weight of >25 year old males
    summary(MALE_older$weight_lb)
    ```

# Common Errors Messages

Everyone eventually encounters a problem with their code. Let's look at some common errors that you may encounter in your R code.

## Error 1

-   The console telling you that R cannot find your function, object, or package

    -   Possible [reasons]{.underline}:

        -   Typos in function, object, or package names

        -   Lines for the function, object, or package weren't run

    -   [Solution:]{.underline} make sure that you correctly spell all your functions, variables, datasets, objects and packages. Note that R is case sensitive too.

## Error 2

-   Your code will either not run or give you a different than expected result if you do not specify or incorrectly specify an argument in the function

    -   Possible [reasons]{.underline}:

        -   Missing or misspelled arguments in R functions

        -   Package conflicts (see Lab 3 Supplementary)

-   [Solution:]{.underline} try taking a look at the documentation (type and run in `?function_name` in your R script) and verify that you have written down the argument names correctly and/or that you’re referencing objects created in the same way that they were originally spelled.

## Error 3

-   The console telling you that R cannot build connection to file(s)

    -   Possible [reasons]{.underline}:

        -   Working directory wasn't set up

        -   Files are saved outside of working directory

        -   Typos in the file path

        -   Slashes in the file path aren't recognized

            -   More often with Windows system (see Lab 1 Supplementary)

-   [Solution:]{.underline} make sure that you correctly set the working directory with everything spelled right. Also, always keep your files organized so that you know where to find them.

<!--points to discuss.. inputting argument names correctly, referring to objects correctly (use the same capitalization and spelling)-->

# Course Project

It is time to start thinking about your course project 🤔

## Purpose

You will be writing an APA style paper to apply skills learned in this course.

-   Hypothesis:

    -   Generate a hypothesis based on the 2 variables chose from course dataset

        -   1 continuous variable and 1 **two-level** categorical variable

-   Analysis:

    -   Carry out an independent samples t-test to test your hypothesis

-   Graph:

    -   Create a graphical display of the chosen continuous variable\
        that compares the two groups in the chosen categorical variable

## Grading

Final lab paper will consist of 15% of your final grade.

There are 2 parts in this paper that come with 2 different deadlines:

::: columns
::: {.column width="50%"}
-   [Part 1](https://canvas.ucdavis.edu/courses/873222/assignments/1159196):

    -   Worth 5% of grade

    -   Due on Feb 26 by 10:00am
:::

::: {.column width="50%"}
-   [Part 2](https://canvas.ucdavis.edu/courses/873222/assignments/1159197):

    -   Worth 10% of grade

    -   Due on Mar 15 by 11:59pm
:::
:::

-   We accept late submissions with a penalty

    -   The penalty is 25% of total points possible per day late

-   Note that any revision made to Part 1 after submission will not be regraded in Part 2

## Resources {.smaller}

All the information needed to get started with the project are up on Canvas under module: **Course Paper - Resources**.

::: columns
::: {.column width="50%"}
-   Dataset:

    -   [Midlife in the United States (MIDUS 3)](https://canvas.ucdavis.edu/courses/873222/pages/information-about-the-midlife-in-the-united-states-midus-3?module_item_id=1759768): information about the project, recruitment, and data collection

        -   [Navigate ICPSR Website](https://canvas.ucdavis.edu/courses/873222/pages/1-introduction-to-icpsr-and-where-youll-locate-and-download-a-data-set-for-the-course-paper?module_item_id=1759762): where MIDUS 3 is hosted

        <!--# use sign in with email to create account with edu email... the SSO portal is so slow and somehow not able to open -->

        -   [Access and download dataset](https://canvas.ucdavis.edu/courses/873222/pages/2-steps-to-access-and-download-the-dataset-for-the-course-paper?module_item_id=1759763): how to find MIDUS 3

            -   You need an ICPSR account to download the dataset. **Create a new account using your @ucdavis.edu email** and do not use the SSO portal.

        -   [Access and download codebook](https://canvas.ucdavis.edu/courses/873222/pages/3-steps-to-access-and-download-the-codebook-for-the-course-data-set?module_item_id=1759764): how to understand variables in MIDUS 3
:::

::: {.column width="50%"}
-   Writing guide: [elements](https://canvas.ucdavis.edu/courses/873222/pages/guide-to-writing-the-course-paper?module_item_id=1759765) of the paper

    -   **Make sure to read very carefully**

<!--# copy and open the link and show them the guide, talk a bit about each elements and page number, ect. -->

-   [Rubric](https://canvas.ucdavis.edu/courses/873222/pages/how-well-grade-the-course-paper-rubric?module_item_id=1759766): Part 1 and Part 2

-   Format: APA 7th edition

    -   [Structure, in-text citations, and references](https://owl.purdue.edu/owl/research_and_citation/apa_style/apa_formatting_and_style_guide/apa_sample_paper.html)

    -   [Tables and figures](https://canvas.ucdavis.edu/courses/873222/pages/tables-and-figures-placing-them-in-your-paper?module_item_id=1759769): tips on placing figures in paper

    -   [MIDUS 3](https://canvas.ucdavis.edu/courses/873222/pages/citation-for-the-midus-3-apa-formatted?module_item_id=1759771): always cite the open dataset being used
:::
:::

# Lab Activity

Now let's try to start preparing the course dataset ✨

## Course Dataset

You will be using the **MIDUS 3** dataset for the course project.

If you have not yet downloaded the dataset and codebook from ICPSR website, take advantage of this lab time to get started!

Instructions are available on Canvas under module: Course Paper - Resources.

::: fragment
You should have the following files ready in the working directory:
:::

-   Dataset: `36346-0001-Data.rda`

    -   .rda is the format for a R data file

-   Codebook: `36346-0001-Codebook-aggregate_data.pdf`

## Activity 1

Once you have the files ready, following the steps and scripts provided in **Learning Module 4** to:

1.  Import the MIDUS 3 dataset into R

2.  Subset the dataset to only include approved variables

3.  Clean the dataset to create independent samples

::: fragment
At the end of subsetting and cleaning, you should have a total of **1732 observations of 87 variables** for the dataset prepared to start the course project.
:::

::: fragment
💡 **Hint**: Check out the "2. Import the course data set" section from Learning Module 4 for guidance with importing data in R.
:::

## Activity 1 (Solution)

<!--# live code during lab, swap echo value when posting announcement -->

::: columns
::: {.column width="50%"}
```{r, eval=F,echo=T}
# Set working directory
setwd("C:\\Users\\Monica\\PSC 103A\\Data")

# load the file
load(file='36346-0001-Data.rda')

# This code has been provided in Learning Module 4
# Let's find it then apply the code
tempdata <- da36346.0001[, c("M2ID",
                             "SAMPLMAJ",
                             "C1PRAGE",
                             "C1PRSEX",
                             "C1PA1",
                             "C1PA2",
                             "C1PA3",
                             "C1PA39",
                             "C1PA59",
                             "C1PDEPAF",
                             "C1PANHED",
                             "C1PDEPRE",
                             "C1PANXIE",
                             "C1PPANIC",
                             "C1PPARTN",
                             "C1PB32A",
                             "C1PD1",
                             "C1PF1",
                             "C1PF12A",
                             "C1SSATIS2",
                             "C1SHLOCS",
                             "C1SAMPLI",
                             "C1SA15",
                             "C1SNEGAF",
                             "C1SNEGPA",
                             "C1SPOSAF",
                             "C1SPOSPA",
                             "C1SBADL2",
                             "C1SIADL",
                             "C1SINTAG",
                             "C1SWSTHI",
                             "C1SBMI",
                             "C1SPWBA1",
                             "C1SPWBE1",
                             "C1SPWBG1",
                             "C1SPWBR1",
                             "C1SPWBU1",
                             "C1SPWBS1",
                             "C1SPWBA2",
                             "C1SPWBE2",
                             "C1SPWBG2",
                             "C1SPWBR2",
                             "C1SPWBU2",
                             "C1SPWBS2",
                             "C1SMPQWB",
                             "C1SMPQSP",
                             "C1SMPQAC",
                             "C1SMPQSC",
                             "C1SMPQSR",
                             "C1SMPQAG",
                             "C1SMPQAL",
                             "C1SMPQCN",
                             "C1SMPQTR",
                             "C1SMPQHA",
                             "C1SOPTIM",
                             "C1SPESSI",
                             "C1SREINT",
                             "C1SACTIV",
                             "C1SPLAN",
                             "C1SVENT",
                             "C1SDENIA",
                             "C1SDISEN",
                             "C1SPRCOP",
                             "C1SEMCOP",
                             "C1SSWBSI",
                             "C1SSWBAO",
                             "C1SSWBSC",
                             "C1SSWBSA",
                             "C1SSYMP",
                             "C1SMNDFU",
                             "C1SLFEDI",
                             "C1SP3",
                             "C1SP4A",
                             "C1SP4B",
                             "C1SP4C",
                             "C1SP4D",
                             "C1SP4E",
                             "C1SP4F",
                             "C1SP4G",
                             "C1SP4H",
                             "C1SP4I",
                             "C1SP4J",
                             "C1SP4K",
                             "C1SP4L",
                             "C1SQ1",
                             "C1SQ4",
                             "C1PA25BS"
)] 

```
:::

::: {.column width="50%"}
```{r,echo=T,eval=F}
psc103Adata <- tempdata[tempdata$SAMPLMAJ %in% c("(01) MAIN RDD", "(04) CITY OVERSAMPLE" ), ]  

# check that the dataframe
# was created correctly
str(psc103Adata)
```
:::
:::

## Activity 2 {.smaller}

Go to the MIDUS 3 codebook and look for variable `C1PA25BS`. Take a moment to read about the variable and try your best to understand it. You don't need to import the codebook into R.

After you know more about the variable:

1.  Describe `C1PA25BS` using functions from Base R

2.  Summarize `C1PA25BS` using a graphical display with proper axis labels

    -   General audience should be able to understand your graph without having to go through the codebook

3.  Ask yourself the question: is `C1PA25BS` normally distributed?

::: fragment
💡 **Hint**: What is the variable measuring? Are there any missing observations in this variable? What is the variable type?
:::

::: {.fragment style="font-size:80%"}
```{r, eval=FALSE, echo=TRUE}
# Looking for SOLUTION? 

## Think about the hints! Revisit previous slides if need to :)
## Try it out yourself!
```
:::

## Activity 3 {.smaller}

Hopefully by now, you have the course dataset ready to go and are more familiar with how to use the dataset and navigate the codebook.

Spend rest of the lab time to start thinking about your hypothesis and look into the relevant variables for the course project.

-   Aagin, you can choose 1 continuous variable and 1 **two-level** categorical variable from the 87 available variables in the dataset.

-   However, please note, you should avoid choosing the following 2 variables: `M2ID` and `SAMPLMAJ`.

    -   They are used to identify participants and subset independent samples for the project.

    -   There isn't much value in them conducting analysis required for the course project.
