---
title: "Pilot_Cleaning"
author: "Xinhui Zhang"
date: "2024-08-08"
output: html_document
---

```{r}
library(tidycode)
library(tibble)
library(dplyr)
library(tidyverse)
library(readr)
library(ggplot2)
```


```{r}
data <- read.csv("Pilot_demographic_data.csv")
```


## randomly assign the number to each person after you used SID to clean the dataset

```{r}
dem_summer_raw <- data %>% select("sis_id", contains(".."))
```

## Rename the data
```{r}
colnames(dem_summer_raw) <- c("SID", "consent", "age", "year", "gender", "first_language", "exp_eng", "confidence", "ethcity", "f_education", "m_education", "lunch_program", "Grant", "Transfer")
```

## consent
```{r}
dem_summer_short <- dem_summer_raw %>%
  mutate(consent = case_when(
    grepl("I do not consent", consent, fixed = TRUE) ~ 0,
    grepl("I consent to participate", consent, fixed = TRUE) ~ 1,
    TRUE ~ 0))
```

##filter
```{r}
dem_summer_short <- dem_summer_short %>%
  filter(consent == 1)
```




## age

dem_summer_clean <- dem_summer_short %>%
  mutate(age = str_remove_all(age, "years old")) %>%
  mutate(age = case_when(
    grepl("I am 20", age, fixed = TRUE) ~ "20",
    grepl("21 years of age at the time of this study", age, fixed = TRUE) ~ "21",
    TRUE ~ age
  ))


##age#2
```{r}
dem_summer_clean <- dem_summer_short %>%
  mutate(age = str_remove_all(age, "[[:space:]]|[[:punct:]]|years old|I am|years of age at the time of this study")) %>% mutate_at(3,as.numeric)

```

## year
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(year = case_when(
    grepl("1st", year, fixed = TRUE) ~ 1,
     grepl("2nd", year, fixed = TRUE) ~ 2,
     grepl("3rd", year, fixed = TRUE) ~ 3,
     grepl("4th", year, fixed = TRUE) ~ 4,
  ))
```


##gender
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(gender = case_when(
    grepl("Woman", gender, fixed = TRUE) ~ 'Woman',
    grepl("Man", gender, fixed = TRUE) ~ 'Man',
    grepl("Non-binary or Genderqueer", gender, fixed = TRUE) ~ 'Other',
    TRUE~NA
  ))
```

##first_language
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(first_language = case_when(
    grepl("English is my first language", first_language, fixed = TRUE) ~ 1,
    grepl("English is not my first language", first_language, fixed = TRUE) ~ 0,
    TRUE~NA
  ))
```

## exp_eng
```{r}
dem_summer_clean <- dem_summer_clean%>%
  mutate(exp_eng = case_when(
    grepl("Some of my education has been in English", exp_eng, fixed = TRUE) ~ 1,
    grepl("About half of my education has been in English", exp_eng, fixed = TRUE) ~ 2,
    grepl("Most of my education has been in English", exp_eng, fixed = TRUE) ~ 3,
    grepl("All or almost all of my academic experience has been in English", exp_eng, fixed = TRUE) ~ 4,
    TRUE ~ NA
  ))
```


## confidence
```{r}
dem_summer_clean <- dem_summer_clean%>%
  mutate(confidence = case_when(
    grepl("I am confident reading more advanced books in English", confidence, fixed = TRUE) ~ 0,
    grepl("I am confident reading very complex information", confidence, fixed = TRUE) ~ 1,
    TRUE ~ NA
  ))
```

## ethcity
```{r}
dem_summer_clean <- dem_summer_clean%>%
  mutate(ethcity = case_when(
    grepl("South Asian,Pacific Islander,Mixed Race", ethcity, fixed = TRUE) ~ 0,
    grepl("Black or African American", ethcity, fixed = TRUE) ~ 1,
    grepl("Caucasian", ethcity, fixed = TRUE) ~ 2, 
    grepl("East or South East Asian", ethcity, fixed = TRUE) ~ 3,
    grepl("Hispanic or Latino", ethcity, fixed = TRUE) ~ 4,
    grepl("Middle Eastern or West Asian", ethcity, fixed = TRUE) ~ 5,
    grepl("Mixed Race", ethcity, fixed = TRUE) ~ 6,
    grepl("Native American",ethcity, fixed = TRUE) ~ 7,
    grepl("South Asian", ethcity, fixed = TRUE) ~ 8,
    TRUE~NA
  ))
```

## f_education
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(f_education = case_when(
    grepl("He left when he graduated from high school (or GED)", f_education, fixed = TRUE) ~ 1, 
    grepl("He left school before he graduated from high school", f_education, fixed = TRUE) ~ 2,
    grepl("He attended some college, but left before he earned a 4-year degree", f_education, fixed = TRUE) ~ 3,
    grepl("He earned a 4-year degree", f_education, fixed = TRUE) ~ 4,
    grepl("He earned a graduate degree (Masters or Ph.D)", f_education, fixed = TRUE) ~ 5,
    TRUE~NA
  ))
```

## m_education
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(m_education = case_when(
    grepl("She left school when she graduated from high school (or GED)", m_education, fixed = TRUE) ~ 1, 
    grepl("She left school before she graduated from high school", m_education, fixed = TRUE) ~ 2,
    grepl("She attended some college, but left before she earned a 4-year degree", m_education, fixed = TRUE) ~ 3,
    grepl("She earned a 4-year degree", m_education, fixed = TRUE) ~ 4,
    grepl("She earned a graduate degree (Masters or Ph.D)", m_education, fixed = TRUE) ~ 5,
    TRUE~NA
  ))
```


## lunch_program
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(lunch_program = case_when(
    grepl("I did not", lunch_program, fixed = TRUE) ~ 0,
    grepl("I don't know", lunch_program, fixed = TRUE) ~ 1,
    grepl("I qualified", lunch_program, fixed = TRUE) ~ 2,
    TRUE~NA
  ))
```


##Pell Grant

```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(Grant = case_when(
    grepl("I do not qualify", Grant, fixed = TRUE) ~ 0,
    grepl("I do qualify", Grant, fixed = TRUE) ~ 1,
    grepl("I don't know", Grant, fixed = TRUE) ~ 2,
    TRUE~NA
  ))
```


## Transfer
```{r}
dem_summer_clean <- dem_summer_clean %>%
  mutate(Transfer = case_when(
    grepl("No", Transfer, fixed = TRUE) ~ 0,
    grepl("Yes", Transfer, fixed = TRUE) ~ 1,
    TRUE~NA
  ))
```

## first_gen
```{r}
dem_summer_clean <- dem_summer_clean %>% mutate(first_gen = case_when(f_education <4 & m_education < 4 ~ 1, f_education >= 4 | m_education >= 4 ~ 0))

dem_summer_clean <- dem_summer_clean %>%  mutate(first_gen = case_when(first_gen == NA & f_education < 4 | m_education < 4 ~ 1, .default = first_gen)) %>% mutate( first_gen = case_when(first_gen == NA & m_education < 4 | f_education < 4 ~ 1, .default = first_gen)) %>% mutate_at(c(1,4,5,6,7,8,9), factor) 
```

## save file
```{r}
write.csv(dem_summer_clean, file = "Pilot_dem_cleaned.csv", row.names = F)
```



```{r}
test <- read.csv("Pilot_dem_cleaned.csv")

test <- test %>% mutate_at(c(1,4, 5), factor)




table <- test %>% group_by(year) %>% summarise(n= n(), mean = mean(age))

hist(test$age)

```

##canvas
```{r}
setwd("~/Documents/GitHub/MC_data_cleaning/pilot data")
```

```{r}
data<- read.csv ("Pilot_canvas_data.csv")
```



```{r}
canvas_data <- data %>% select("SIS.User.ID", contains("Exam.1..892860."), contains("Exam.2..892861."), contains("Exam.3..892862."), contains("Exam.4..892863."), contains("Exam.5..892864."), contains("Final.Exam..892865."),"Prep.Participation..up.to.250.points..Final.Points", contains("Extra.Credit.Final.Points"), contains("Exam.Corrections")) %>% mutate_at(-c(1), as.numeric)
```

```{r}
colnames(canvas_data)<- c("SID", "exam1", "exam2", "exam3","exam4","exam5","final_exam", "prep_p_raw", "extra_credit", "e_correct")
```

## p_p_final
```{r}
canvas_data$p_p_final <- canvas_data$prep_p_raw
canvas_data$p_p_final[canvas_data$prep_p_raw >= 250]<- 250
```

## drop the lowest exam score
```{r}
canvas_data <- canvas_data %>% filter(!is.na(SID))
canvas_data[is.na(canvas_data)] <- 0
canvas_exam <- canvas_data %>% select(contains("exam"))
canvas_exam$lowest <- apply(canvas_exam, 1, min)
canvas_exam$lowest <- canvas_exam$lowest * -1
canvas_data$exam_total <- apply(canvas_exam, 1, sum)
```

```{r}
final_grade_calc <- canvas_data %>% select("extra_credit", "p_p_final", "exam_total")
canvas_clean <- canvas_data %>% 
  mutate(final_grade = apply(final_grade_calc, 1, sum)) %>%
  mutate(opt_in = case_when(e_correct == 0 ~ 0, e_correct > 0 ~ 1)) 
```


```{r}

exam_col <- canvas_clean %>% select(contains("exam"), -exam_total)
```

```{r}
canvas_final <- canvas_clean %>% mutate(exam_total = (exam_total/750)*100) %>% mutate(final_grade = (final_grade/1000)*100)
```


## write document
```{r}
write.csv(canvas_final, file = "Pilot_canvas_cleaned.csv", row.names = F)
```


Final_data <- left_join(dem_data, canvas, by = SID) # only fills in the data from canvas for SIDs that exist in the dem data set --- leaves out students who don't consent

## Combine Data
```{r}
setwd("~/Documents/GitHub/MC_data_cleaning/pilot data")
```


## Unit 1
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/pilot data/Unit 1"
Unit1 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
results_list <- list()
```

```{r}
for (file in Unit1) {
  unit1 <- read.csv(file)
   unit1 <- unit1 %>% select("SID","View.Count", "Status", 14, 16, 17, 19, 23, 28, 29, 30, 31)
   q_names <- c("SID", "views1", "Status", "h0", "h1", "h2", "pv_op", "ov_op", "claim_ex", "temp", "alt_ex", "interpret")
   colnames(unit1) <- q_names
   unit1 <- unit1 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
    results_list[[basename(file)]] <- unit1
}
unit1_full <- bind_rows(results_list, .id = "source")
```

```{r}
write.csv(unit1_full, file = "unit1_written.cleaned.csv", row.names = F)
```

## Unit 2
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/pilot data/Unit 2"
Unit2 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
results_list <- list()
```

```{r}
for (file in Unit2) {
  unit2 <- read.csv(file)
   unit2 <- unit2 %>% select("SID", "View.Count", "Status", 14, 18, 19, 22, 23, 24, 26, 29)
   q_names <- c("SID", "views2", "Status", "pv_op", "pv_cv", "ov_op", "ov_cv", "effect", "ov_reliability", "h1", "interpret")
   colnames(unit2) <- q_names
   unit2 <- unit2 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
    results_list[[basename(file)]] <- unit2
}
unit2_full <- bind_rows(results_list, .id = "source")
```

```{r}
write.csv(unit2_full, file = "unit2_written.cleaned.csv", row.names = F)
```

##Unit 3
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/pilot data/Unit 3"
Unit3 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
results_list <- list()
```

```{r}
for (file in Unit3) {
  unit3 <- read.csv(file)
   unit3 <- unit3 %>% select("SID", "View.Count", "Status", 14, 18, 22, 23, 24, 25, 28)
   q_names <- c("SID", "views3", "Status", "pv_op", "pv_cv", "ov_cv", "internal1", "internal2", "confound", "interpret")
   colnames(unit3) <- q_names
   unit3 <- unit3 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
   
    results_list[[basename(file)]] <- unit3
}
unit3_full <- bind_rows(results_list, .id = "source")
```

```{r}
write.csv(unit3_full, file = "unit3_written.cleaned.csv", row.names = F)
```

##Unit 4
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/pilot data/Unit 4"
Unit4 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
results_list <- list()
```

```{r}
for (file in Unit4) {
  unit4 <- read.csv(file)
   unit4 <- unit4 %>% select("SID", "View.Count", "Status", 19, 20, 23, 24, 25, 29, 30, 31, 32)
   q_names <- c("SID", "views4", "Status", "design_ex", "ov_op", "ov_cv", "bias_ex", "confound", "IRB", "sampling", "external", "replicate")
   colnames(unit4) <- q_names
   unit4 <- unit4 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
    results_list[[basename(file)]] <- unit4
}
unit4_full <- bind_rows(results_list, .id = "source")
```

```{r}
write.csv(unit4_full, file = "unit4_written.cleaned.csv", row.names = F)
```


##Unit 5
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/pilot data/Unit 5"
Unit5 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
results_list <- list()
```

```{r}
for (file in Unit5) {
  unit5 <- read.csv(file)
   unit5 <- unit5 %>% select("SID", "View.Count", "Status", 14, 19, 23, 24, 25, 29, 30, 31)
   q_names <- c("SID", "views5", "Status", "pv_op", "pv_cv", "construct_ex", "confound", "maturation", "interpret", "external", "replication")
   colnames(unit5) <- q_names
   unit5 <- unit5 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
    results_list[[basename(file)]] <- unit5
}
unit5_full <- bind_rows(results_list, .id = "source")
```

```{r}
write.csv(unit5_full, file = "unit5_written.cleaned.csv", row.names = F)
```

```{r}
canvas_final$SID <- as.factor(canvas_final$SID)
```

```{r}
Final_data <- left_join(dem_summer_clean, canvas_final, by = "SID")
```


## p_tot1
```{r}
library(dplyr)
unit1_short <- read.csv("unit1_written.cleaned.csv", sep = ",")
```

```{r}
unit1_calc <- unit1_short %>% select(4:12)
unit1_short <- unit1_short %>%
  mutate(written = rowSums(unit1_calc, na.rm = TRUE))
```

```{r}
unit1_final <- unit1_short %>% mutate(p_tot1 = (written/85)*100) 
```

```{r}
unit1_end <- unit1_final %>% select("SID", "views1", "p_tot1")
```

```{r}
unit1_end$SID <- as.factor(unit1_end$SID)
full_data <- left_join(Final_data, unit1_end, by = "SID" )
```

## p_tot2
```{r}
library(dplyr)
unit2_short <- read.csv("unit2_written.cleaned.csv", sep = ",")
```

```{r}
unit2_calc <- unit2_short %>% select(4:11)
unit2_short <- unit2_short %>%
  mutate(written = rowSums(unit2_calc, na.rm = TRUE))
```

```{r}
unit2_final <- unit2_short %>% mutate(p_tot2 = (written/90)*100) 
```

```{r}
unit2_end <- unit2_final %>% select("SID", "views2", "p_tot2")
```

```{r}
unit2_end$SID <- as.factor(unit2_end$SID)
full_data <- left_join(full_data, unit2_end, by = "SID" )
```

##p_tot3
```{r}
library(dplyr)
unit3_short <- read.csv("unit3_written.cleaned.csv", sep = ",")
```

```{r}
unit3_calc <- unit3_short %>% select(4:10)
unit3_short <- unit3_short %>%
  mutate(written = rowSums(unit3_calc, na.rm = TRUE))
```

```{r}
unit3_final <- unit3_short %>% mutate(p_tot3 = (written/75)*100) 
```

```{r}
unit3_end <- unit3_final %>% select("SID", "views3", "p_tot3")
```

```{r}
unit3_end$SID <- as.factor(unit3_end$SID)
full_data <- left_join(full_data, unit3_end, by = "SID" )
```

#p_tot4
```{r}
library(dplyr)
unit4_short <- read.csv("unit4_written.cleaned.csv", sep = ",")
```

```{r}
unit4_calc <- unit4_short %>% select(4:12)
unit4_short <- unit4_short %>%
  mutate(written = rowSums(unit4_calc, na.rm = TRUE))
```

```{r}
unit4_final <- unit4_short %>% mutate(p_tot4 = (written/90)*100) 
```

```{r}
unit4_end <- unit4_final %>% select("SID", "views4", "p_tot4")
```

```{r}
unit4_end$SID <- as.factor(unit4_end$SID)
full_data <- left_join(full_data, unit4_end, by = "SID" )
```

## p_tot5
```{r}
library(dplyr)
unit5_short <- read.csv("unit5_written.cleaned.csv", sep = ",")
```

```{r}
unit5_calc <- unit5_short %>% select(4:11)
unit5_short <- unit5_short %>%
  mutate(written = rowSums(unit5_calc, na.rm = TRUE))
```

```{r}
unit5_final <- unit5_short %>% mutate(p_tot5 = (written/80)*100) 
```

```{r}
unit5_end <- unit5_final %>% select("SID", "views5", "p_tot5")
```

```{r}
unit5_end$SID <- as.factor(unit5_end$SID)
full_data <- left_join(full_data, unit5_end, by = "SID" )
```