---
title: "2024 Data"
author: "Xinhui Zhang"
date: "2024-09-04"
output: html_document
---

```{r}
library(tidycode)
library(tibble)
library(dplyr)
library(tidyverse)
library(readr)
```

```{r}
setwd("~/Documents/GitHub/MC_data_cleaning/2024 Data")
```


```{r}
dem_raw_data <- read.csv("Demographics Survey Student Analysis Report.csv", sep = ",")
```

```{r}
short_data <- dem_raw_data %>% select("sis_id", "attempt", contains(".."))
```

```{r}
colnames(short_data) <- c("SID", "attempt", "consent", "age", "year", "gender", "int", "first_language", "academic_exp", "eng_level", "ethnicity", "f_edu", "m_edu", "p_relation", "financial", "program", "pell_grant", "minutes", "hours", "transfer")
```
##consent
```{r}
dem_short <- short_data %>%
  mutate(consent = case_when(
    grepl("I do not consent", consent, fixed = TRUE) ~ 0,
    grepl("I consent to participate", consent, fixed = TRUE) ~ 1,
    TRUE ~ 0)) 
```

```{r}
dem_short <- dem_short %>%
  filter(consent == 1)
```

##year
```{r}
dem_short <- dem_short %>%
  mutate(year = case_when(
    grepl("Freshman", year, fixed = TRUE) ~ 1,
    grepl("Sophomore", year, fixed = TRUE) ~ 2, 
    grepl("Junior", year, fixed = TRUE) ~ 3,
    grepl("Senior", year, fixed = TRUE) ~ 4,
    TRUE ~ NA
  ))
```

## gender
```{r}
dem_short <- dem_short %>%
  mutate(gender = case_when(
    grepl("Man", gender, fixed = TRUE) ~ 1, 
    grepl("Woman", gender, fixed = TRUE) ~ 2,
    grepl("Non-binary or Genderqueer", gender, fixed = TRUE) ~ 3,
    TRUE ~ NA
    ))
```

##int
```{r}
dem_short <- dem_short %>%
  mutate(int = case_when(
    grepl("Yes, I am an international student", int, fixed = TRUE) ~ 0,
    grepl("No, I am not an international student", int, fixed = TRUE) ~ 1,
    TRUE ~ NA
  ))
```

##first_language
```{r}
dem_short <- dem_short %>%
  mutate(first_language = case_when(
    grepl("English is my first language", first_language, fixed = TRUE) ~ 0,
    grepl("English is not my first language", first_language, fixed = TRUE) ~ 1,
    TRUE ~ NA
  ))
```

## academic_exp
```{r}
dem_short <- dem_short %>%
  mutate(academic_exp = str_remove_all(academic_exp, "%"))
```

##eng_level
```{r}
dem_short <- dem_short %>%
  mutate(eng_level = case_when(
    grepl("I am not confident reading in English", eng_level, fixed = TRUE) ~ 0,
    grepl("I am confident reading simple information in English", eng_level, fixed = TRUE) ~ 1,
    grepl("I am confident reading simple books in English", eng_level, fixed = TRUE) ~ 2,
    grepl("I am confident reading moderate books in English", eng_level, fixed = TRUE) ~ 3,
    grepl("I am confident reading difficult books in English", eng_level, fixed = TRUE) ~ 4,
    grepl("I am confident reading advanced books in English", eng_level, fixed = TRUE) ~ 5,
    grepl("I am confident reading very complex information in English", eng_level, fixed = TRUE) ~ 6,
    TRUE ~ NA
  ))
```

##ethnicity
```{r}
dem_short <- dem_short %>% 
  mutate(ethnicity = case_when(
    grepl("Black or African American", ethnicity, fixed = TRUE) ~ 0,
    grepl("Mixed Race", ethnicity, fixed = TRUE) ~ 1,
    grepl("Black or African American,Hispanic or Latino", ethnicity, fixed = TRUE) ~ 2,
    grepl("Caucasian", ethnicity, fixed = TRUE) ~ 3,
    grepl("East or South East Asian", ethnicity, fixed = TRUE) ~ 4,
    grepl("Hispanic or Latino", ethnicity, fixed = TRUE) ~ 5,
    grepl("Middle Eastern or West Asian", ethnicity, fixed = TRUE) ~ 6,
    grepl("Native American or American Indian", ethnicity, fixed = TRUE) ~ 7,
    grepl("North or Central Asian", ethnicity, fixed = TRUE) ~ 8,
    grepl("South Asian", ethnicity, fixed = TRUE) ~ 9,
    TRUE ~ NA
  ))
```

## f_edu
```{r}
dem_short <- dem_short %>% 
  mutate(f_edu = case_when(
    grepl("He never attended school", f_edu, fixed = TRUE) ~ 0,
    grepl("He left when he graduated from high school (or GED)", f_edu, fixed = TRUE) ~ 1,
    grepl("He left school before he graduated from high school", f_edu, fixed = TRUE) ~ 2,
    grepl("He attended some college, but left before he earned a 4-year degree", f_edu, fixed = TRUE) ~ 3,
    grepl("He earned a 4-year degree", f_edu, fixed = TRUE) ~ 4,
    grepl("He earned a graduate degree (Masters or Ph.D)", f_edu, fixed = TRUE) ~ 5,
    TRUE ~ NA
  ))
```

## m_edu
```{r}
dem_short <- dem_short %>% 
  mutate(m_edu = case_when(
    grepl("She never attended school", m_edu, fixed = TRUE) ~ 0,
    grepl("She left school when she graduated from high school (or GED)", m_edu, fixed = TRUE) ~ 1,
    grepl("She left school before she graduated from high school", m_edu, fixed = TRUE) ~ 2,
    grepl("She attended some college, but left before she earned a 4-year degree", m_edu, fixed = TRUE) ~ 3,
    grepl("She earned a 4-year degree", m_edu, fixed = TRUE) ~ 4,
    grepl("She earned a graduate degree (Masters or Ph.D)", m_edu, fixed = TRUE) ~ 5,
    TRUE ~ NA
  ))
```

## first_gen
```{r}
dem_short <- dem_short %>% 
  mutate(first_gen = case_when(
    f_edu < 4 & m_edu < 4 ~ 1,
    f_edu >= 4 | m_edu >= 4 ~ 0
  ))

dem_short <- dem_short %>% 
  mutate(first_gen = case_when(
    first_gen == NA & f_edu < 4 | m_edu < 4 ~ 1, .default = first_gen
  )) %>% mutate_at(21, factor)
```

##p_relation
```{r}
dem_short <- dem_short %>% 
  mutate(p_relation = case_when(
    grepl("Divorced", p_relation, fixed = TRUE) ~ 0,
    grepl("Single", p_relation, fixed = TRUE) ~ 1,
    grepl("Seperated", p_relation, fixed = TRUE) ~ 2,
    grepl("Together", p_relation, fixed = TRUE) ~ 3,
    TRUE ~ NA
  ))
```

## financial
```{r}
dem_short <- dem_short %>% 
  mutate(financial = case_when(
    grepl("No support", financial, fixed = TRUE) ~ 1,
    grepl("Very little support", financial, fixed = TRUE) ~ 2,
    grepl("A little support", financial, fixed = TRUE) ~ 3,
    grepl("Some support", financial, fixed = TRUE) ~ 4,
    grepl("Halfway supported", financial, fixed = TRUE) ~ 5,
    grepl("Mostly supported", financial, fixed = TRUE) ~ 6,
    grepl("Fully supported", financial, fixed = TRUE) ~ 7,
    TRUE ~ NA
  ))
```

##program
```{r}
dem_short <- dem_short %>% 
  mutate(program = case_when(
    grepl("I did not qualify for 'free or reduced cost lunch' at all in high school", program, fixed = TRUE) ~ 0,
    grepl("I don't know if I qualified for a 'free or reduced cost lunch' program", program, fixed = TRUE) ~ 1,
     grepl("I qualified for 'free or reduced cost lunch' for some of high school", program, fixed = TRUE) ~ 2,
    grepl("I qualified for 'free or reduced cost lunch' for all or most of high school", program, fixed = TRUE) ~ 3,
    TRUE ~ NA
  ))
```

##pell_grant
```{r}
dem_short <- dem_short %>% 
  mutate(pell_grant = case_when(
    grepl("I do not qualify for a Pell Grant", pell_grant, fixed = TRUE) ~ 0,
    grepl("I do qualify for a Pell Grant", pell_grant, fixed = TRUE) ~ 1,
    grepl("I don't know if I qualify for a Pell Grant", pell_grant, fixed = TRUE) ~ 2,
    TRUE ~ NA
  ))
```

##transfer
```{r}
dem_short <- dem_short %>% 
  mutate(transfer = case_when(
    grepl("No", transfer, fixed = TRUE) ~ 0,
    grepl("Yes", transfer, fixed = TRUE) ~ 1,
    TRUE ~ NA
  ))
```

##save files
```{r}
write.csv(dem_short, file = "dem_2024_cleaned.csv", row.names = F)
```

## canvas
```{r}
raw_data <- read.csv(file = "WQ_2024_canvas_data.csv")
short_data <- raw_data %>% select("SIS.User.ID", "Exam.1..1154283.", "Exam.2..1154284.", "Exam.3..1154285.", "Exam.4..1154286.", "Exam.5..1154287.", "Final.Exam..1154289.", "Prep.Participation..up.to.250.points..Final.Points", "Extra.Credit.Final.Points", "Internal.Validity.in.Practice..1154290.")%>% mutate_at(-c(1), as.numeric)
```
```{r}
colnames(short_data) <- c("SID", "exam1", "exam2","exam3","exam4","exam5","final_exam", "prep_p_raw", "extra_credit", "e_correct")
```

##p_p_final
```{r}
short_data$p_p_final <- short_data$prep_p_raw
short_data$p_p_final[short_data$prep_p_raw >= 250] <- 250
```

## drop the lowest exam score
```{r}
short_data<- short_data %>% filter(!is.na(SID))
short_data[is.na(short_data)] <- 0
exam_data <- short_data %>% select(contains("exam"))
exam_data$lowest <- apply(exam_data, 1, min)
exam_data$lowest <- exam_data$lowest * -1
short_data$exam_total <- apply(exam_data, 1, sum)
```

```{r}
final_grade_calc <- short_data %>% select("extra_credit", "p_p_final", "exam_total")
data_clean <- short_data %>% mutate(final_grade = apply(final_grade_calc, 1, sum)) %>% mutate(opt_in = case_when(e_correct == 0 ~ 0, e_correct > 0 ~ 1))
```

```{r}
# data_clean <- data_clean %>% mutate_at(c(2:12),~na_if(.,0) )
exam_col <- data_clean %>% select(contains("exam"), -exam_total)
```

```{r}
div <- function(x)((x/150)*100)
final_data <- data_clean %>% mutate_at(colnames(exam_col), div) %>% mutate(exam_total = (exam_total/750)*100) %>% mutate(final_grade = (final_grade/1000)*100)
```

```{r}
write.csv(final_data, file = "canvas_2024_cleaned.csv", row.names = F )
```


## combine the dataset
## Combine Dem & Grades
```{r}
grades <- read.csv(file ="canvas_2024_cleaned.csv")

dem <- read.csv("dem_2024_cleaned.csv")

full_grades <- grades %>% select(-"SID")

full_data <- full_join(dem,grades, by = "SID")
```


##Exchange the column number of 21st and 22nd in 1b
```{r}
unit1b <- read.csv("Unit_1_Exam_Version_Set_Scores/Exam_1B_scores.csv")
```

```{r}
unit1b <- unit1b[, c(1:20, 22, 21, 23:ncol(unit1b))]
```

```{r}
write.csv(unit1b, "Exam_1B_scores.csv", row.names = F)
```


##Unit 1 loop
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/2024 Data/Unit_1_Exam_Version_Set_Scores"
Exam1 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)

```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam1) {
  # Read the CSV file
  exam1 <- read.csv(file)
  
  # Select the required columns
  exam1 <- exam1 %>% 
    select("SID","View.Count", "Status", 13, 15, 17, 21, 26, 27)
  
  # Rename the columns
  q_names <- c("SID", "views1", "Status", "h0", "h1", "pv_op", "ov_op", "claim_ex", "interpret")
  colnames(exam1) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam1 <- exam1 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam1
}

# Combine all results into a single data frame
Exam1_full <- bind_rows(results_list, .id = "source")


```


save files
```{r}
write.csv(Exam1_full, "Unit1_scores_cleaned.csv", row.names = F)
```


##Unit2

##Unit 2 loop
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/2024 Data/Exam_2_Version_Set_Scores"
Exam2 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam2) {
  # Read the CSV file
  exam2 <- read.csv(file)
  
  # Select the required columns
  exam2 <- exam2 %>% 
    select("SID","View.Count", "Status", 13, 17, 20, 24)
  
  # Rename the columns
  q_names <- c("SID", "views2", "Status", "pv_op", "pv_cv", "ov_cv", "interpret")
  colnames(exam2) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam2 <- exam2 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam2
}

# Combine all results into a single data frame
Exam2_full <- bind_rows(results_list, .id = "source")
```


save files
```{r}
write.csv(Exam2_full, "Unit2_scores_cleaned.csv", row.names = F)
```


##Unit 3
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/2024 Data/Exam_3_Version_Set_Scores"
Exam3 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam3) {
  # Read the CSV file
  exam3 <- read.csv(file)
  
  # Select the required columns
  exam3 <- exam3 %>% 
    select("SID","View.Count", "Status", 13, 17, 23, 28)
  
  # Rename the columns
  q_names <- c("SID", "views3", "Status", "pv_def", "pv_cv", "internal2", "interpret")
  colnames(exam3) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam3 <- exam3 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam3
}

# Combine all results into a single data frame
Exam3_full <- bind_rows(results_list, .id = "source")
```


save files
```{r}
write.csv(Exam3_full, "Unit3_scores_cleaned.csv", row.names = F)
```


##Unit4
```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/2024 Data/Exam_4_Version_Set_Scores"
Exam4 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam4) {
  # Read the CSV file
  exam4 <- read.csv(file)
  
  # Select the required columns
  exam4 <- exam4 %>% 
    select("SID","View.Count", "Status", 19, 22, 23, 24, 29) ##the 23rd column is appear in many other datasets but 4a
  
  # Rename the columns
  q_names <- c("SID", "views4", "Status", "ov_op", "ov_cv", "internal", "confound", "external")
  colnames(exam4) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam4 <- exam4 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam4
}

# Combine all results into a single data frame
Exam4_full <- bind_rows(results_list, .id = "source")
```

#save files
```{r}
write.csv(Exam4_full, "Unit4_scores_cleaned.csv", row.names = F)
```




## the numbers of columns of 4a and 4b are different, thus I am not be able to get the deleted version for Unit4 rn

##Unit 5

```{r}
library(dplyr)
file_directory <- "~/Documents/GitHub/MC_data_cleaning/2024 Data/Exam_5_Version_Set_Scores"
Exam5 <- list.files(file_directory, pattern = "*.csv", full.names = TRUE)
```

```{r}
# Create an empty list to store the results
results_list <- list()
```

```{r}
# Iterate over each file
for (file in Exam5) {
  # Read the CSV file
  exam5 <- read.csv(file)
  
  # Select the required columns
  exam5 <- exam5 %>% 
    select("SID","View.Count", "Status", 20, 23, 24, 29) ##the 25th column is appear in many other datasets but 5a
  
  # Rename the columns
  q_names <- c("SID", "views5", "Status", "ov_op", "ov_cv", "confound", "interpretation")
  colnames(exam5) <- q_names
  
  # Filter out rows where the status is "Missing" and remove the status column if it exists
  exam5 <- exam5 %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
  
  # Add the processed data to the results list
  results_list[[basename(file)]] <- exam5
}

# Combine all results into a single data frame
Exam5_full <- bind_rows(results_list, .id = "source")
```

#save files
```{r}
write.csv(Exam5_full, "Unit5_scores_cleaned.csv", row.names = F)
```


##Unit5a
```{r}
unit5b <- read.csv("Exam_5_Version_Set_Scores/Exam_5B_scores.csv")
```

```{r}
unit5b<- unit5b %>% select("SID","View.Count", "Status", 20, 23, 24, 29) 
q_names <- c("SID", "views1", "Status", "ov_op", "ov_cv", "internal", "interpretation")
colnames(unit5b) <- q_names
unit5b <- unit5b %>% filter(Status != "Missing") %>% select(-"Status") %>%  filter(SID != "#N/A") %>% filter(SID != "dropped")
```

```{r}
write.csv(unit5b, file = "Unit_5b_cleaned.csv", row.names = F)
```





## p_tot1
```{r}
library(dplyr)
exam1_short <- read.csv("Unit1_scores_cleaned.csv", sep = ",")
```

```{r}
exam1_calc <- exam1_short %>% select(4:9)
exam1_short <- exam1_short %>%
  mutate(written = rowSums(exam1_calc, na.rm = TRUE))
```

```{r}
exam1_final <- exam1_short %>% mutate(p_tot1 = (written/60)*100) 
```

```{r}
exam1_end <- exam1_final %>% select("SID", "views1", "p_tot1")
```

```{r}
full_data <- left_join(full_data, exam1_end, by = "SID" )
```


##p_tot2
```{r}
library(dplyr)
exam2_short <- read.csv("Unit2_scores_cleaned.csv", sep = ",")
```

```{r}
exam2_calc <- exam2_short %>% select(4:7)
exam2_short <- exam2_short %>%
  mutate(written = rowSums(exam2_calc, na.rm = TRUE))
```

```{r}
exam2_final <- exam2_short %>% mutate(p_tot2 = (written/55)*100) 
```

```{r}
exam2_end <- exam2_final %>% select("SID", "views2", "p_tot2")
```

```{r}
full_data <- left_join(full_data, exam2_end, by = "SID" )
```

##p_tot3
```{r}
library(dplyr)
exam3_short <- read.csv("Unit3_scores_cleaned.csv", sep = ",")
```

```{r}
exam3_calc <- exam3_short %>% select(4:7)
exam3_short <- exam3_short %>%
  mutate(written = rowSums(exam3_calc, na.rm = TRUE))
```

```{r}
exam3_final <- exam3_short %>% mutate(p_tot3 = (written/50)*100) 
```

```{r}
exam3_end <- exam3_final %>% select("SID", "views3", "p_tot3")
```

```{r}
full_data <- left_join(full_data, exam3_end, by = "SID" )
```


##p_tot4
```{r}
library(dplyr)
exam4_short <- read.csv("Unit4_scores_cleaned.csv", sep = ",")
```

```{r}
exam4_calc <- exam4_short %>% select(4:7)
exam4_short <- exam4_short %>%
  mutate(written = rowSums(exam4_calc, na.rm = TRUE))
```

```{r}
exam4_final <- exam4_short %>% mutate(p_tot4 = (written/40)*100) 
```

```{r}
exam4_end <- exam4_final %>% select("SID", "views4", "p_tot4")
```

```{r}
full_data <- left_join(full_data, exam4_end, by = "SID" )
```

##p_tot5
```{r}
library(dplyr)
exam5_short <- read.csv("Unit5_scores_cleaned.csv", sep = ",")
```

```{r}
exam5_calc <- exam5_short %>% select(4:7)
exam5_short <- exam5_short %>%
  mutate(written = rowSums(exam5_calc, na.rm = TRUE))
```

```{r}
exam5_final <- exam5_short %>% mutate(p_tot5 = (written/40)*100) 
```

```{r}
exam5_end <- exam5_final %>% select("SID", "views5", "p_tot5")
```

```{r}
full_data <- left_join(full_data, exam5_end, by = "SID" )
```



## Deidentify the data 

```{r}
original_id <- full_data %>% select("SID")
```

```{r}
set.seed(123)
original_id$anon_id <- sample(100000000:999999999, nrow(original_id), replace = FALSE)
```

```{r}
full_data <- left_join(full_data, original_id, by = "SID")
```

```{r}
anon_data <- full_data %>%
  select(2:45)
```

```{r}
id_modified <- anon_data %>%
  relocate(anon_id, .before = 1)
```

```{r}
write.csv(id_modified, "2024_full_data_cleaned.csv", row.names = F)
```

